### 2022-08-16 LaTeX/Vorlage Latex - Eng.tex
Adds LaTeX, fixes dates of data, standardizes variables before PCA

%Schriftgröße, Dokumentformat, Dokumenttyp
\documentclass[11pt,a4paper]{article}
%Einstellungen der Seitenränder
\usepackage[left=3cm,right=4cm,top=2cm,bottom=2cm,includeheadfoot]{geometry}
%neue Rechtschreibung und Formelsatz
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{amsmath,amssymb,amsthm}
%Graphiken
\usepackage{graphicx}
\usepackage{float}
%Zeilenabstand
\usepackage{setspace}\onehalfspacing
%Aufzählungen
\usepackage{paralist}
%Abkürzungen
\usepackage{acronym}
%Tabelle
\usepackage{multirow}
%Kopf- und Fußzeile
\usepackage{fancyhdr}
%Fußnotenkram
\usepackage{footnote}
\usepackage{hyperref}
\usepackage[hang]{footmisc}
\usepackage{graphics}
\usepackage{glossaries}
\setlength{\footnotesep}{0.25 cm}

\begin{document}
% Keine Seitenzahlen im Vorspann
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%% Titelblatt der Arbeit %%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}				
	\begin{center}
Professorship for XXX\\
Institute of XXX\\
Faculty of Business, Economics and Social Sciences\\
Kiel University \\
		\vspace{5cm}

		\LARGE{ \bf{Density Forecasts of the S\&P using Markov-Switching Models}}
		\vspace{2cm}

		\large{\bf{Seminar paper}}\\
		Submission Date: XX.XX.XXXX
		\vspace{1.5cm}

\begin{flushleft}
\vfill
	Author: Adrian Beer
	Subject:\\
	Semester:3
	Module: Seminar in Econometrics
	Stu-Email-Adress:\\
	Matriculation number:\\
	\vspace{1cm}
	First Assessor:\\
	Second Assessor:
\end{flushleft}

	\end{center}

\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%% Inhaltsverzeichnis %%%%%%%%%%%%%%%%%%%%%%%

\newpage
	\tableofcontents
	\newpage

% Kopf- und Fußzeile definieren 
\pagestyle{fancy}					
\fancyhf{}								
%Kopfzeile rechts bzw. außen			
\fancyhead[R]{}							 
%Linie oben								 
\renewcommand{\headrulewidth}{0pt}	 
%Fußzeile mittig					 
\fancyfoot[R]{\thepage}				 
%Linie unten										
\renewcommand{\footrulewidth}{0pt}	 
%Seitenzahlen ab hier						 
\pagenumbering {Roman} 
\setcounter{page}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Figures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{section}{Figure directory}
\listoffigures

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Tables %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{section}{Table directory}
\listoftables
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Acronyms %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{List of Acronyms} %Bitte alphabetisch ordnen!
\addcontentsline{toc}{section}{Abbreviation directory}
\rule[0pt]{0mm}{10pt}
\noindent Include an abbreviation directory if you use more than three uncommon abbreviations.\\

\begin{tabular}{l l l}

	% B
	BLL && Bayesian Local Likelihood\\
	BR&&Bounded Rationality\\
	% D
	DSGE&&Dynamic Stochastic General Equilibrium\\

\end{tabular}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Symbols %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{List of Symbols} 
\addcontentsline{toc}{section}{Symbol directory}
\noindent Include a symbol directory if you use more than three uncommon abbreviations.
	\begin{tabular}{l l}
		\textbf{} & \\
		$\pi$ & rate of inflation\\
		$i$ & nominal interest rate \\
		$r$ & real interest rate \\
		$M$ & money stock \\

	\end{tabular}\\ \vspace{1cm}

\newpage

% Kopf- und Fußzeile definieren %%
\pagestyle{fancy}						
\fancyhf{}								
%Kopfzeile rechts bzw. außen			
\fancyhead[R]{}							 
%Linie oben								 
\renewcommand{\headrulewidth}{0pt}	 
%Fußzeile mittig					 
\fancyfoot[R]{\thepage}				 
%Linie unten										
\renewcommand{\footrulewidth}{0pt}	 
%Seitenzahlen ab hier						 
\pagenumbering {arabic}
\onehalfspacing	
\section{Introduction}
Markov chain processes can be useful for identifying regimes in the past as well as estimating the current regime. %% why is this important
If the Markov model describes the data generating process well, it can also be used to simulate synthetic time series and potential future paths. %% why is this important

We test 3 models: 
1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
2. A markov-switching model without indicators
3. A markov-switching model with indicators

\section{Background}

There are two main ways to learn the parameters of a HMM model: Expectation-Maximization Algorithms (EM) such as Baum-Welch. And Markov Chain Monte Carlo methods (MCMC) such as the Metropolis-Hastings or Gibbs Sampling algorithm.

The EM Algorithm makes use of the forward-backward algorithm.

Given a HMM model we can deduce estimates of the hidden state via the Viterbi algorithm.

\section{HMM with time-varying transition probabilities}
Our goal is to maximize the incomplete data log-likelihood $\log f(y \mid X ; \theta)=\log \sum_{s_{1}=1}^{2} \sum_{s_{2}=1}^{2} \ldots \sum_{s_{T}=1}^{2} f(y, s \mid X ; \theta)$ which is not feasible to compute (complexity). \\
Hence we maximize the expected value of the complete data log-likelihood $\log f(y, s \mid X ; \theta)$. Let $Y_t$ be the natural filtration of $Y$ and $\mathbb{X}_t$.
\section{First chapter of main text}

Divide your text into chapters (1; 2; 3; ...), sections (1.1; 1.2; 1.3; ...) and subsections (2.1.1; 2.1.2; 2.1.3; ...). A bullet point 2.1.1 is nonsensical unless a bullet point 2.1.2 follows. Give all chapters, sections, and subsections expressive headings.
\newpage

\subsection{First section of first chapter of main text}
This section is nonsensical unless a section 2.2 follows.

\subsubsection{First subsection}
This subsection is nonsensical unless a section 2.1.2 follows. You may include a table in this section. Label the table and indicate the source including the page number like you would in the continuous text. The contents of the table below are taken from the highly cited Smets \& Wouters (2007: 597).
\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
		\begin{tabular}{cccccccccccccc}
			\hline \hline
			&&&&&&&&&&&&&\\
			&	Base& & $\xi_p=0.1$ & &$\xi_w=0.1$ & & $\iota_p\approx0.0$&& $\iota_w\approx0.0$ &&$\phi=0.1$ && $\lambda=0.1$ \\
			\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} 
			\textit{Est. Mode}&&&&&&&&&&&&&\\
			$\varphi$ & 5.48&& 4.41 && 2.78 && 5.45 &&5.62 && 0.1 && 1.26\\
			$\sigma_c$& 1.39 && 1.31 && 1.80 && 1.43 && 1.42 && 2.78&& 2.90\\
			$\sigma_l$&1.92&&1.48&&0.25&&1.91&&1.91&&5.24&&1.21\\
			$\lambda$&0.71 && 0.70 && 0.34 && 0.70&& 0.71&& 0.12 && 0.10\\
			$\xi_w$&0.73&& 0.55&&0.10&&0.75&&0.75&&0.89&&0.73\\
			$\xi_p$&0.65&&0.10&&0.48&&0.66&&0.69&&0.86&&0.62\\
			$\iota_p$&0.22&&0.84&&0.24&&0.01&&0.24&&0.08&&0.21\\
			$\iota_w$&0.59&&0.71&&0.68&&0.61&&0.01&&0.39&&0.61\\
			$r_\pi$&2.03&&2.15&&2.15&&2.01&&2.01&&2.03&&2.24\\
			$r_y$&0.08&&0.08&&0.08&&0.08&&0.09&&0.23&&0.12\\
			$r_{\Delta y}$&0.22&&0.21&&0.25&&0.22&&0.22&&0.30&&0.29\\
			&&&&&&&&&&&&&\\
			\textit{Marg. LH} & && && && && && &&\\
			&-923&&-975&&-973&&-918&&-927&&-1084&&-959\\
			&&&&&&&&&&&&&\\
			\hline \hline
	\end{tabular}}
	\caption[Example table (short description)]{An example table. Describe it shortly. Source: Smets \& Wouters (2007): 597.}
\end{table}
\newpage
 \subsubsection{Second Subsection}
You may want to include a figure here. Label the figure and include the source. You may also want to include a second figure that you created yourself.
 \begin{figure}[H]
 	\includegraphics[width=\textwidth]{example_figure}
 	\caption[Short description]{IRFs. SW baseline model with standard calibration (black line, appendix table 8), with low habits in consumption (blue line, table 1) and with low capital adjustment cost (blue line, table 1). Source: Own simulation.}
 \end{figure}
\newpage
\subsection{Second section of first chapter of main text}
This section follows section 2.1 with its subsections. Make it clear how sec-tions and chapters in your work link together. Some introductory and guiding sentences may help the reader and yourself not to lose track of the line of reasoning.

\newpage

\section{Second chapter of main text}

The main text can consist of several chapters, sections and subsections.\\
Use paragraphs to divide the body text within the (sub) chapters into mean-ingful sections. Paragraphs that are longer than one page are usually too long. The reader will not remember upon reaching the end of the paragraph what the main message was. On the other hand, a paragraph that consists of only one sentence is likely too short.\\
If you include illustrations, tables and / or equations in the text, explain them to the reader and describe the results in the text. When using symbols in the text, include their meaning (for example, the money stock M).

\newpage

\section{Conclusion}
End your work with a chapter in which you summarize your findings, formulate some theses, or point out unsolved problems.\\
Before submitting your work, check the following (non-exhaustive) checklist to see if you have met the basic requirements of a well-crafted seminar pa-per, bachelor or master thesis.
\begin{itemize}
	\item Does the text still contain spelling or punctuation errors?
	\item Do you use a fluent and understandable way of expression?
	\item Are words, passages or entire pages missing?
	\item Does the table of contents (and other directories) match the structure of the text and page numbers?
	\item Is the bibliography complete? (Delete bibliography entries that you do not cite!)
	\item Are all references to literature, figures and appendix correct? Did you forget any references?
	\item Is the layout (headings, text formatting, etc.) clear and consistent?
	\item Did you include all necessary components of a scientific paper?
	\item Did you correctly number figures, tables, footnotes, equation?

\end{itemize}
\newpage

% Kopf- und Fußzeile definieren 
\pagestyle{fancy}						
\fancyhf{}								
%Kopfzeile rechts bzw. außen			
\fancyhead[R]{}							 
%Linie oben								 
\renewcommand{\headrulewidth}{0pt}	 
%Fußzeile mittig					 
\fancyfoot[R]{\thepage}				 
%Linie unten										
\renewcommand{\footrulewidth}{0pt}	 
%Seitenzahlen ab hier						 
\pagenumbering {Roman} 
\setcounter{page}{5}
\newpage\clearpage

\newpage
\addcontentsline{toc}{section}{Bibliography}
\section*{Bibliography}
In the bibliography, you list all the sources that you use and therefore cite in the text (sources that you have read but not cited should not be listed). Sort the entries in the bibliography, listed according to a consistent style, alphabetically by last name.
\begin{itemize}
	\item[] Adolfson, M.; Las\'een, S.; Lind\'e, J. (2007): Bayesian Estimation of an Open Economy DSGE Model with Incomplete Pass-Through, \textit{Journal of International Economics} 72 (2): 481-511.
 \item[] Christiano, L.; Eichenbaum, M.; Evans, C. (2005): Nominal Rigidities and the Dynamic Effects of a Shock to Monetary Policy, \textit{Journal of Political Economy} 113 (1): 1-45.
 \item[] Hommes, C.; Makarewicz, T.; Massaro, D.; Smits, T. (2017): Genetic Algorithm Learning in a New Keynesian Macroeconomic Setup, \textit{Journal of Evolutionary Economics} 27: 1133-1155.
	\item[] Smets, F.; Wouters, R. (2007): Shocks and Frictions in US Business Cycles: A Bayesian DSGE Approach, \textit{The American Economic Review} 97: 
	\item[] Wieland, V.; Wolters, M. (2012): Forecasting and Policy Making, \textit{IMFS Working Paper Series} No. 62.
\end{itemize}

\newpage

\addcontentsline{toc}{section}{Appendix}
\begin{appendix}
	The appendix contains tables, data, questionnaires, proofs, derivations, etc., which you consider merely additional information and negatively affect the reading flow in the main text. Do not use the appendix for outsourcing text that does not fit into the main text due to page restrictions. Only include an appendix when needed.
	\section{Equality of 1 and 2}
	\label{proof:1equal2}
	\begin{align}
	x^2 &= x^2 \\
	x^2 - x^2 &= x^2 - x^2 \\
	x^2 - x^2 &= x^2 - x^2 + x^2 - x^2	\\
	x\cdot\left(x-x\right) &= \left(x+x\right)\cdot\left(x-x\right)	\\
	x &= \left(x+x\right)	\\
	1 &= 2	\hspace{1cm} q.e.d.
	\end{align}
\section{Latex examples}
\begin{table}
	\centering\rotatebox{90}{%
		\resizebox{\textheight}{!}{%
			\begin{tabular}{lccccccccccccccccccc}
				\hline \hline
				&&&&&&&&&&&&&&&&&&&\\
				\textit{Correlation}&	Animal Spirits & & Output $y_t$ & &Consumption $c_t$ & & Investment $i_t$&& Hours Worked $l_t$ &&Capital Arbitrage $q_t$ && Inflation $\pi_t$&& Rental Rate $r^k_t$&&Wage $w_t$&&Interest Rate $r_t$\\
				\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} \cline{16-16} \cline{18-18} \cline{20-20} 
				&&&&&&&&&&&&&&&&&&&\\
				Animal Spirits&1&&-&&-0.6520**&&0.6831**&&0.3197**&&0.3259**&&0.3918**&&-0.4220&&0.1646&&-\\
				Output $y_t$&-&&1&&0.8265**&&0.4859**&&0.8559**&&0.7169**&&-0.6618**&&0.8279**&&0.4404**&&-0.5713**\\
				Consumption $c_t$&-0.6520**&&0.8265**&&1&&0.5300**&&0.6896**&&0.9628**&&-0.7739**&&0.6663**&&0.3654**&&-0.7699**\\
				Investment $i_t$&0.6831**&&0.4854**&&0.5300**&&1&&0.4229**&&0.4724**&&-0.2134*&&0.2835**&&0.1891**&&-0.2100*\\
				Hours Worked $l_t$&0.3197**&&0.8559**&&0.6896**&&0.4229**&&1&&0.5279**&&-0.4433**&&0.8108**&&0.2382*&&-0.3638**\\
				Capital Arbitrage $q_t$&0.3259**&&0.7169**&&0.9628**&&0.4724**&&0.5279**&&1&&-0.7767**&&0.5515**&&0.3607**&&-0.7936**\\
				Inflation $\pi_t$&0.3918**&&-0.6618**&&-0.7739**&&-0.2134*&&-0.4433**&&-0.7767**&&1&&-0.5601**&&-0.4131**&&0.9647**\\
				Rental Rate $r^k_t$&-0.4220&&0.8279**&&0.6663**&&0.2835**&&0.8108**&&0.5515**&&-0.5601**&&1&&0.7393**&&-0.4796**\\
				Wage $w_t$&0.1646&&0.4404**&&0.3654**&&0.1891**&&0.2382*&&0.3607**&&-0.4131**&&0.7393**&&1&&-0.3712**\\
				Interest Rate $r_t$&-&&-0.5713**&&-0.7699**&&-0.2100*&&-0.3638**&&-0.7936**&&0.9647**&&-0.4796**&&-0.3712**&&1\\
				&&&&&&&&&&&&&&&&&&&\\
				\hline \hline
	\end{tabular}}}
	\caption[Rotated table]{Rotated table. \\ **: 99\% Confidence; *: 95\% Confidence.}
\end{table}
Some aligned equations
	\begin{align}
	\widetilde{\text{E}}_tv_{t+1}&= \underbrace{(\omega_t^{v,sta}+\omega_t^{v,anc}(\varOmega+\varUpsilon(1-\varpi)))}_{\Lambda^v_t}v_{t-1} \notag \\&-\omega_t^{v,anc}\varOmega v_{t-2}+\underbrace{\omega_t^{v,anc}(1-\varpi)(1-\varUpsilon)}_{\Theta^v_t}\widetilde{\text{E}}^{anc}_{t-1}v_{t}+\omega_t^{v,anc}\varpi v^{avg.}_{t-1}
	\end{align}
	and matrices that have no tag 
	\begin{align}
	\textbf{A}_{10\times10}= \begin{pmatrix}
	A_{1,5\times5} & A_{2,5\times5} \\
	A_{3,5\times5} & A_{4,5\times5}
	\end{pmatrix}, \quad \widetilde{\textbf{B}}_{t,10\times10}= \begin{pmatrix}
	B_{1,5\times5} & B_{2,5\times5} \\
	B_{3,5\times5} & B_{4,5\times5}
	\end{pmatrix}\notag \\ \widetilde{\textbf{C}}_{t,10\times10}=\begin{pmatrix}
	C_{1,5\times5} & C_{2,5\times5} \\
	C_{3,5\times5} & C_{4,5\times5}
	\end{pmatrix}, \quad \textbf{D}_{t,10\times9}= \begin{pmatrix}
	D_{1,5\times5} & D_{2,5\times4} \\
	D_{3,5\times5} & D_{4,5\times4}
	\end{pmatrix}\notag \\
	\widetilde{\textbf{F}}_{t,10\times10}=\begin{pmatrix}
	F_{1,5\times5} & F_{2,5\times5} \\
	F_{3,5\times5} & F_{4,5\times5}
	\end{pmatrix}, \quad 	\widetilde{\textbf{G}}_{t,10\times10}= \begin{pmatrix}
	G_{1,5\times5} & G_{2,5\times5} \\
	G_{3,5\times5} & G_{4,5\times5}
	\end{pmatrix}\notag 
	\end{align}
	of the system 
   \begin{align}
   \textbf{V}_t &= \textbf{A}^{-1}\left[\widetilde{\textbf{B}}_t\textbf{V}_{t-1}+\widetilde{\textbf{C}}_t\textbf{V}_{t-2}+\widetilde{\textbf{F}}_t\widetilde{\text{E}}^{anc}_{t-1}\widetilde{\textbf{V}}_{t}+\widetilde{\textbf{G}}_t\textbf{V}^{avg.}_{t-1}+\textbf{D}\textbf{e}_t\right],
   \end{align}
   \newpage
	\section{Questionaire}
	Here you can include a questionnaire that you used in your paper.
\end{appendix}
\newpage
\section*{Affirmation}
I hereby declare that I have composed my Bachelor/Master's thesis / Seminar paper 
\textit{"title"} independently using only those resources mentioned, 
and that I have as such identified all passages which I have 
taken from publications verbatim or in substance. I agree that the work will be reviewed using plagiarism testing software.
Neither 
this paper, nor any extract of it, has been previously 
submitted to an examining authority, in this or a similar 
form.\\ \\
\textit{Only for Bacherlor’s and Master’s theses with included CD:}\\
I have ensured that the written version of this thesis is 
identical to the version saved on the enclosed storage 
medium. \\\\\\

\begin{flushright}
$\overline{~~~~~~~~~~~~~~~\mbox{(Date, Signature)}~~~~~~~~~~~~~~~}$
\end{flushright}
\end{document}

### 2022-08-16 dataset_preprocessor.py

@@ -7,7 +7,7 @@ from sklearn.decomposition import PCA
 
 from config import data_dir
 
-# Schiller S&P TR
+# Extract data from Shiller's dataset.
 # ----------------
 path = os.path.join(data_dir , "ie_data.xls")
 xls = pd.ExcelFile(path, engine="xlrd")
@@ -21,17 +21,25 @@ data.iloc[:, 0] = data.iloc[:, 0].apply(lambda x: x.replace(".1", ".10") if len(
 data.iloc[:, 0] = data.iloc[:, 0].apply(lambda x: str(x)[:7]+".01")
 data['Datetime'] = pd.to_datetime(data.iloc[:, 0], format="%Y.%m.%d")
 data = data.set_index('Datetime').sort_index()
+# Data for some month-date represents average of that month and so it should be mapped to the last day of the month.
+data = data.resample("M").last()
 
 
-data = (data.iloc[:, 1])# / data.iloc[:, 4]
-data = pd.to_numeric(data)
-SP_TR_df = data
+PRICE = pd.to_numeric(data.loc[:, "Price.1"])  # Real Total Return Prices
+CPI = pd.to_numeric(data.loc[:, "CPI"])  # CPI
 
-print(np.log(SP_TR_df).diff().dropna().describe())
-plt.hist(np.log(SP_TR_df).diff().dropna(), bins="scott", title="Distribution of S&P log returns")
+PRICE.to_pickle(os.path.join(data_dir, f"PRICE.pkl"))
+
+#INFLATION = CPI.pct_change()
+#INFLATION.name = "Inflation"
+
+print(np.log(PRICE).diff().dropna().describe())
+plt.hist(np.log(PRICE).diff().dropna(), bins="scott")
+plt.title("Distribution of S&P log returns")
 plt.show()
 
-plt.plot(np.log(SP_TR_df))
+plt.plot(np.log(PRICE))
+plt.title("Log of Total Return S&P")
 plt.show()
 
 # FRED Data sets
@@ -42,58 +50,79 @@ for f_name in ["BAA", "AAA"]:
     df = pd.read_csv(path)
     df["DATE2"] = pd.to_datetime(df.pop("DATE"))
     df = df.set_index("DATE2")
+    # The data points for monthly FRED time series initially "<M>.01", but they are only available at the end of the
+    # month, so we need to reassign the dates to the end of the month.
+    df = df.resample("M").last()
     dfs.append(df)
-
[…]

### 2022-08-21 markov_model.R
Seems to be some bug in time_varying_markov_model... can't fix. Try R package

@@ -1,0 +1,2 @@
+#HMM
+library(depmixS4)

### 2022-08-21 setup.py

@@ -1,0 +1,6 @@
+from setuptools import setup
+from Cython.Build import cythonize
+
+setup(
+    ext_modules = cythonize("time_varying_markov_model.pyx")
+)

### 2022-08-21 time_varying_markov_model.py

@@ -16,8 +16,11 @@ assert X.index.equals(Y.index)
 # Parameters etc.
 T = len(Y)
 #theta
-beta0 = (-0.01, -0.01)
-beta1 = (0.01, 0.01)
+beta0 = (-0.5, -0.5)
+beta1 = (0.5, 0.5)
+
+alpha0 = (0.005, 0.04)
+alpha1 = (-0.002, 0.1)
 
 # probability of state1 being 0
 p_first_state_0 = 0.8
@@ -29,9 +32,9 @@ def conditional_density(y, s: bool, alpha0, alpha1):
     # phi0 is the parameter  vector for state 0
     # phi1 is the parameter vector for state 1
     if s == 1:
-        return norm.pdf(y, loc=alpha1)
+        return norm.pdf(y, loc=alpha1[0], scale=alpha1[1])
     else:
-        return norm.pdf(y, loc=alpha0)
+        return norm.pdf(y, loc=alpha0[0], scale=alpha0[1])
 
 
 def transition_probabilities(x, beta0, beta1):
@@ -43,8 +46,8 @@ def transition_probabilities(x, beta0, beta1):
 
 
 # 1. Calculate sequence of filtered marginal densities and trans. probs.
-FMYD1 = conditional_density(Y, 0, 0.5, -0.5)
-FMYD2 = conditional_density(Y, 1, 0.5, -0.5)
+FMYD1 = conditional_density(Y, 0, alpha0, alpha1)
+FMYD2 = conditional_density(Y, 1, alpha0, alpha1)
 FMYD_df = pd.DataFrame({0:FMYD1, 1:FMYD2}, index=Y.index) # FMYD.loc[t, <state_t>]
 FMYD = FMYD_df.to_numpy()
 
@@ -54,7 +57,7 @@ TPM = TPM.reshape(TPM.shape[0], 2, 2)
 TPM_df = pd.DataFrame(index=X.index, columns=pd.MultiIndex.from_product([[0,1], [0,1]]), data=TPM.reshape(TPM.shape[0], 4))
 assert (TPM_df.sum(axis=1) - 2 < 0.001).all()
 # TPM.loc[t, (<state_t>, <state_t+1>)])
-
+print(TPM_df.head())
 
 # 2. Calculate Filtered joint state probabilities
 # 2a. Calculate joint conditional distribution of (y_t, s_t, s_{t-1})
@@ -96,33 +99,44 @@ assert ((FILT_STATE_PROB[1:].sum(axis=1) - 1) < 0.001).all()
[…]

### 2022-08-21 dataset_preprocessor.py
start using MSGARCH

@@ -4,7 +4,7 @@ import numpy as np
 import pandas as pd
 from matplotlib import pyplot as plt
 from sklearn.decomposition import PCA
-
+import feather
 from config import data_dir
 
 # Extract data from Shiller's dataset.
@@ -27,7 +27,9 @@ data = data.resample("M").last()
 
 PRICE = pd.to_numeric(data.loc[:, "Price.1"])  # Real Total Return Prices
 log_returns = np.log(PRICE).diff()
-
+print(log_returns.describe())
+plt.plot(np.abs(log_returns))
+plt.show()
 
 CPI = pd.to_numeric(data.loc[:, "CPI"])  # CPI
 
@@ -105,6 +107,7 @@ print(np.corrcoef(log_returns[-length:], component))
 # Aligning exogeneous indicator with log_returns and export
 common_idx = log_returns.index.intersection(component.index)
 log_returns.loc[common_idx].to_pickle(os.path.join(data_dir, f"LOG_RETURNS.pkl"))
+
 X = component.loc[common_idx].copy().to_frame()
 X.insert(0, "Intercept", 1)
 X.to_pickle(os.path.join(data_dir, f"X.pkl"))

### 2022-08-21 markov_model.R

@@ -1,2 +1,50 @@
+# Import Dataset
+library("quantmod")
+
+start <- as.Date("1950-01-01")
+end <- as.Date("2022-08-21")
+df <- quantmod::getSymbols("^SP500TR", src = "yahoo", from = start, to = end, auto.assign = FALSE)
+price = df[, "SP500TR.Close"]
+lret = diff(log(price))[-1,]
+plot(lret)
+
+
+split_idx = round(length(lret)*0.9)
+train_y = lret[1:split_idx]
+test_y = lret[(1+split_idx):length(lret)]
+
+real_vola = abs(lret*100)
+
+
+
 #HMM
-library(depmixS4)
+library("MSGARCH")
+
+# SINGLE REGIME
+
+
+# MULTI-REGIME (non-switching shape)
+ms2.garch.n <- CreateSpec(variance.spec = list(model = c("tGARCH", "tGARCH")),
+                   distribution.spec = list(distribution = c("sged", "sged")))
+summary(ms2.garch.n)
+fit.ml <- FitML(spec = ms2.garch.n, data = train_y*100)
+summary(fit.ml)
+
+fit.mcmc <- FitMCMC(spec = ms2.garch.n, data = train_y)
+summary(fit.mcmc)
+
+# Forecasting
+last_date = 10
+pred <- predict(fit.ml, nahead = 5, do.return.draw = TRUE, newdata=test_y[0:last_date])
+
+date = index(pred$draw[1, ])
+date
+lret[date]
+
+
+pred <- predict(fit.mcmc, nahead = 1, do.return.draw = FALSE)
+pred
+
+
+
+

### 2022-08-23 LaTeX/Vorlage Latex - Eng.tex
Working on Latex and MSGARC R file.

@@
 \setlength{\footnotesep}{0.25 cm}
+
+% MAKE subsubsubsection possible
+\usepackage{titlesec}
+
+\setcounter{secnumdepth}{4}
+
+\titleformat{\paragraph}
+{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\titlespacing*{\paragraph}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Acronyms %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{List of Acronyms} %Bitte alphabetisch ordnen!
-\addcontentsline{toc}{section}{Abbreviation directory}
-\rule[0pt]{0mm}{10pt}
-\noindent Include an abbreviation directory if you use more than three uncommon abbreviations.\\
-
-\begin{tabular}{l l l}
-
-	% B
-	BLL && Bayesian Local Likelihood\\
-	BR&&Bounded Rationality\\
-	% D
-	DSGE&&Dynamic Stochastic General Equilibrium\\
-
-\end{tabular}
-
-\newpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Symbols %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We test 3 models: 
-1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
-2. A markov-switching model without indicators
-3. A markov-switching model with indicators
-
 \section{Background}
@@
 
-\section{HMM with time-varying transition probabilities}
-Our goal is to maximize the incomplete data log-likelihood $\log f(y \mid X ; \theta)=\log \sum_{s_{1}=1}^{2} \sum_{s_{2}=1}^{2} \ldots \sum_{s_{T}=1}^{2} f(y, s \mid X ; \theta)$ which is not feasible to compute (complexity).
-\\
-Hence we maximize the expected value of the complete data log-likelihood $\log f(y, s \mid X ; \theta)$. Let $Y_t$ be the natural filtration of $Y$ and $\mathbb{X}_t$.
+Our goal is to maximize the incomplete data log-likelihood 
+$$\log f(y \mid X ; \theta)=\log \sum_{s_{1}=1}^{2} \sum_{s_{2}=1}^{2} \ldots \sum_{s_{T}=1}^{2} f(y, s \mid X ; \theta)$$ which is not feasible to compute (complexity).
+
+\subsection{Markov-Switching Models}
+
+\subsubsection{Exogeneous Variables}
+\paragraph{Time-varying transition probabilities}
+Most HMMs are trained based on an purely endogeneous variables.
+One way to introduce exogeneous variables X into the HMM is by using them to estimate time-varying transition probabilities.
+This concept has been introduced by Diebold et al.
+\cite{diebold_regime_1993} together with closed form solutions for Gaussian state probability distributions.
+Since the complexity of calculating the expected likelihood for the EM algorithm in this setting is squared in the number of observations, maximizing it numerically with respect to the parameters is computationally not feasible.
+Since no closed form solutions to the maximization step for any fat-tailed distributions are available in this setting, this is currently not suited to model financial market data.
+
+\paragraph{State-space model/ DFM-MSs}
+Another way to integrate outside information is to use state space models.
+In this setting the state is represented by one or more so called dynamic factors whose behaviour is specified in the state equation and its relation to the variable of interest in the output equation.
+The usefulness of this approach depends on two factors: the dynamic factor has to be somewhat predictable and
+needs to explain the output variable reasonably well. The state space model can be learned using the Kalman filters in Gaussian settings or using MCMC methods otherwise.
+
+\subsection{Financial Market Data}
+
+\subsubsection{Stylized Facts about returns and volatility}
+Volatility is standard deviation of the log returns.
+Fat-tailed. Power-law. Daily vs Monthly frequencies.
+
+\subsubsection{GARCH}
+GARCH (General Autoregressive Conditional Heteroskedasticity) has been popular in order to forecast the volatility of indices.
+It tries to explain the observation that the volatility of an asset tends to cluster, i.e.
+periods with high volatility are followed by periods with high volatility.
+however the model fails to explain many phenomena which are observed, like the fat-tailedness of drawdown periods and depths (cite Robert Frey).
+The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
+$$y_{l} \mid\left(s_{l}=k, \mathcal{I}_{l-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$
+$\mathcal{D}$ being some zero-mean distribution, the variance h and shape parameters $\xi$.
+For short time-periods the zero-mean specification is justified most of the time.
+$s_t$ is the state at time t is modeled by a Markov chain.\\
+
+A GARCH(1,1) model has the form $h_{k, t} \equiv \alpha_{0, k}+\alpha_{1, k} y_{t-1}^{2}+\beta_{k} h_{k, t-1}$.
+Similar to an ARMA model which tries specify the conditional mean, the GARCH model tries to specify the conditional variance.
+The lagged squared return term can be interpreted as a proxy for the realized variance in the last observation period.
+Long periods of high variance can be modeled by increasing the intercept $\beta$.\\
+
+Many extensions of the GARCH model exist, like (todo).
+The TGARCH e.g.
+tries to incorporate the observation that variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
+$$h_{k, t}^{1 / 2} \equiv \alpha_{0, k}+\left(\alpha_{1, k} \mathbb{I}\left\{y_{t-1} \geq 0\right\}-\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}+\beta_{k} h_{k, t-1}^{1 / 2}$$
+
 \section{First chapter of main text}
+We try to predict S\&P index using
 
-Divide your text into chapters (1; 2; 3; ...), sections (1.1; 1.2; 1.3; ...) and subsections (2.1.1; 2.1.2; 2.1.3; ...).
-A bullet point 2.1.1 is nonsensical unless a bullet point 2.1.2 follows.
-Give all chapters, sections, and subsections expressive headings.
-\newpage
+\subsection{Experiment description}
+We compare the performance of 3 models: 
+1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
+2. A markov-switching model without indicators
+3. A markov-switching model with indicators
 
-\subsection{First section of first chapter of main text}
-This section is nonsensical unless a section 2.2 follows.
+\subsection{Data set}
 
-\subsubsection{First subsection}
-This subsection is nonsensical unless a section 2.1.2 follows.
-You may include a table in this section.
-Label the table and indicate the source including the page number like you would in the continuous text.
-The contents of the table below are taken from the highly cited Smets \& Wouters (2007: 597).
-\begin{table}[H]
-	\centering
-	\resizebox{\textwidth}{!}{%
-		\begin{tabular}{cccccccccccccc}
-			\hline \hline
-			&&&&&&&&&&&&&\\
-			&	Base& & $\xi_p=0.1$ & &$\xi_w=0.1$ & & $\iota_p\approx0.0$&& $\iota_w\approx0.0$ &&$\phi=0.1$ && $\lambda=0.1$ \\
-			\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} 
-			\textit{Est. Mode}&&&&&&&&&&&&&\\
-			$\varphi$ & 5.48&& 4.41 && 2.78 && 5.45 &&5.62 && 0.1 && 1.26\\
-			$\sigma_c$& 1.39 && 1.31 && 1.80 && 1.43 && 1.42 && 2.78&& 2.90\\
-			$\sigma_l$&1.92&&1.48&&0.25&&1.91&&1.91&&5.24&&1.21\\
-			$\lambda$&0.71 && 0.70 && 0.34 && 0.70&& 0.71&& 0.12 && 0.10\\
-			$\xi_w$&0.73&& 0.55&&0.10&&0.75&&0.75&&0.89&&0.73\\
-			$\xi_p$&0.65&&0.10&&0.48&&0.66&&0.69&&0.86&&0.62\\
-			$\iota_p$&0.22&&0.84&&0.24&&0.01&&0.24&&0.08&&0.21\\
-			$\iota_w$&0.59&&0.71&&0.68&&0.61&&0.01&&0.39&&0.61\\
-			$r_\pi$&2.03&&2.15&&2.15&&2.01&&2.01&&2.03&&2.24\\
-			$r_y$&0.08&&0.08&&0.08&&0.08&&0.09&&0.23&&0.12\\
-			$r_{\Delta y}$&0.22&&0.21&&0.25&&0.22&&0.22&&0.30&&0.29\\
-			&&&&&&&&&&&&&\\
-			\textit{Marg. LH} & && && && && && &&\\
-			&-923&&-975&&-973&&-918&&-927&&-1084&&-959\\
-			&&&&&&&&&&&&&\\
-			\hline \hline
-	\end{tabular}}
-	\caption[Example table (short description)]{An example table. Describe it shortly. Source: Smets \& Wouters (2007): 597.}
-\end{table}
-\newpage
- \subsubsection{Second Subsection}
-You may want to include a figure here. Label the figure and include the source. You may also want to include a second figure that you created yourself.
- \begin{figure}[H]
- 	\includegraphics[width=\textwidth]{example_figure}
- 	\caption[Short description]{IRFs.
-SW baseline model with standard calibration (black line, appendix table 8), with low habits in consumption (blue line, table 1) and with low capital adjustment cost (blue line, table 1).
-Source: Own simulation.}
- \end{figure}
-\newpage
-\subsection{Second section of first chapter of main text}
-This section follows section 2.1 with its subsections.
-Make it clear how sec-tions and chapters in your work link together.
-Some introductory and guiding sentences may help the reader and yourself not to lose track of the line of reasoning.
-
-\newpage
-
-\section{Second chapter of main text}
-
-The main text can consist of several chapters, sections and subsections.\\
-Use paragraphs to divide the body text within the (sub) chapters into mean-ingful sections.
-Paragraphs that are longer than one page are usually too long.
-The reader will not remember upon reaching the end of the paragraph what the main message was.
-On the other hand, a paragraph that consists of only one sentence is likely too short.\\
-If you include illustrations, tables and / or equations in the text, explain them to the reader and describe the results in the text.
-When using symbols in the text, include their meaning (for example, the money stock M).
-
-\newpage
+\subsection{Results}
 
 \section{Conclusion}
-End your work with a chapter in which you summarize your findings, formulate some theses, or point out unsolved problems.\\
-Before submitting your work, check the following (non-exhaustive) checklist to see if you have met the basic requirements of a well-crafted seminar pa-per, bachelor or master thesis.
-\begin{itemize}
-	\item Does the text still contain spelling or punctuation errors?
-	\item Do you use a fluent and understandable way of expression?
-	\item Are words, passages or entire pages missing?
-	\item Does the table of contents (and other directories) match the structure of the text and page numbers?
-	\item Is the bibliography complete? (Delete bibliography entries that you do not cite!)
-	\item Are all references to literature, figures and appendix correct? Did you forget any references?
-	\item Is the layout (headings, text formatting, etc.) clear and consistent?
-	\item Did you include all necessary components of a scientific paper?
-	\item Did you correctly number figures, tables, footnotes, equation?
 
-\end{itemize}
 \newpage
@@
 Sort the entries in the bibliography, listed according to a consistent style, alphabetically by last name.
-\begin{itemize}
-	\item[] Adolfson, M.; Las\'een, S.; Lind\'e, J. (2007): Bayesian Estimation of an Open Economy DSGE Model with Incomplete Pass-Through, \textit{Journal of International Economics} 72 (2): 481-511.
- \item[] Christiano, L.; Eichenbaum, M.; Evans, C. (2005): Nominal Rigidities and the Dynamic Effects of a Shock to Monetary Policy, \textit{Journal of Political Economy} 113 (1): 1-45.
- \item[] Hommes, C.; Makarewicz, T.; Massaro, D.; Smits, T. (2017): Genetic Algorithm Learning in a New Keynesian Macroeconomic Setup, \textit{Journal of Evolutionary Economics} 27: 1133-1155.
-	\item[] Smets, F.; Wouters, R. (2007): Shocks and Frictions in US Business Cycles: A Bayesian DSGE Approach, \textit{The American Economic Review} 97: 
-	\item[] Wieland, V.; Wolters, M. (2012): Forecasting and Policy Making, \textit{IMFS Working Paper Series} No. 62.
-\end{itemize}
+
+\bibliography{References}
+\bibliographystyle{Alpha}
 
 \newpage
-
-\addcontentsline{toc}{section}{Appendix}
-\begin{appendix}
-	The appendix contains tables, data, questionnaires, proofs, derivations, etc., which you consider merely additional information and negatively affect the reading flow in the main text.
-Do not use the appendix for outsourcing text that does not fit into the main text due to page restrictions.
-Only include an appendix when needed.
-	\section{Equality of 1 and 2}
-	\label{proof:1equal2}
-	\begin{align}
-	x^2 &= x^2 \\
-	x^2 - x^2 &= x^2 - x^2 \\
-	x^2 - x^2 &= x^2 - x^2 + x^2 - x^2	\\
-	x\cdot\left(x-x\right) &= \left(x+x\right)\cdot\left(x-x\right)	\\
-	x &= \left(x+x\right)	\\
-	1 &= 2	\hspace{1cm} q.e.d.
-	\end{align}
-\section{Latex examples}
-\begin{table}
-	\centering\rotatebox{90}{%
-		\resizebox{\textheight}{!}{%
-			\begin{tabular}{lccccccccccccccccccc}
-				\hline \hline
-				&&&&&&&&&&&&&&&&&&&\\
-				\textit{Correlation}&	Animal Spirits & & Output $y_t$ & &Consumption $c_t$ & & Investment $i_t$&& Hours Worked $l_t$ &&Capital Arbitrage $q_t$ && Inflation $\pi_t$&& Rental Rate $r^k_t$&&Wage $w_t$&&Interest Rate $r_t$\\
-				\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} \cline{16-16} \cline{18-18} \cline{20-20} 
-				&&&&&&&&&&&&&&&&&&&\\
-				Animal Spirits&1&&-&&-0.6520**&&0.6831**&&0.3197**&&0.3259**&&0.3918**&&-0.4220&&0.1646&&-\\
-				Output $y_t$&-&&1&&0.8265**&&0.4859**&&0.8559**&&0.7169**&&-0.6618**&&0.8279**&&0.4404**&&-0.5713**\\
-				Consumption $c_t$&-0.6520**&&0.8265**&&1&&0.5300**&&0.6896**&&0.9628**&&-0.7739**&&0.6663**&&0.3654**&&-0.7699**\\
-				Investment $i_t$&0.6831**&&0.4854**&&0.5300**&&1&&0.4229**&&0.4724**&&-0.2134*&&0.2835**&&0.1891**&&-0.2100*\\
-				Hours Worked $l_t$&0.3197**&&0.8559**&&0.6896**&&0.4229**&&1&&0.5279**&&-0.4433**&&0.8108**&&0.2382*&&-0.3638**\\
-				Capital Arbitrage $q_t$&0.3259**&&0.7169**&&0.9628**&&0.4724**&&0.5279**&&1&&-0.7767**&&0.5515**&&0.3607**&&-0.7936**\\
-				Inflation $\pi_t$&0.3918**&&-0.6618**&&-0.7739**&&-0.2134*&&-0.4433**&&-0.7767**&&1&&-0.5601**&&-0.4131**&&0.9647**\\
-				Rental Rate $r^k_t$&-0.4220&&0.8279**&&0.6663**&&0.2835**&&0.8108**&&0.5515**&&-0.5601**&&1&&0.7393**&&-0.4796**\\
-				Wage $w_t$&0.1646&&0.4404**&&0.3654**&&0.1891**&&0.2382*&&0.3607**&&-0.4131**&&0.7393**&&1&&-0.3712**\\
-				Interest Rate $r_t$&-&&-0.5713**&&-0.7699**&&-0.2100*&&-0.3638**&&-0.7936**&&0.9647**&&-0.4796**&&-0.3712**&&1\\
-				&&&&&&&&&&&&&&&&&&&\\
-				\hline \hline
-	\end{tabular}}}
-	\caption[Rotated table]{Rotated table. \\ **: 99\% Confidence; *: 95\% Confidence.}
-\end{table}
-Some aligned equations
-	\begin{align}
-	\widetilde{\text{E}}_tv_{t+1}&= \underbrace{(\omega_t^{v,sta}+\omega_t^{v,anc}(\varOmega+\varUpsilon(1-\varpi)))}_{\Lambda^v_t}v_{t-1} \notag \\&-\omega_t^{v,anc}\varOmega v_{t-2}+\underbrace{\omega_t^{v,anc}(1-\varpi)(1-\varUpsilon)}_{\Theta^v_t}\widetilde{\text{E}}^{anc}_{t-1}v_{t}+\omega_t^{v,anc}\varpi v^{avg.}_{t-1}
-	\end{align}
-	and matrices that have no tag 
-	\begin{align}
-	\textbf{A}_{10\times10}= \begin{pmatrix}
-	A_{1,5\times5} & A_{2,5\times5} \\
-	A_{3,5\times5} & A_{4,5\times5}
-	\end{pmatrix}, \quad \widetilde{\textbf{B}}_{t,10\times10}= \begin{pmatrix}
-	B_{1,5\times5} & B_{2,5\times5} \\
-	B_{3,5\times5} & B_{4,5\times5}
-	\end{pmatrix}\notag \\ \widetilde{\textbf{C}}_{t,10\times10}=\begin{pmatrix}
-	C_{1,5\times5} & C_{2,5\times5} \\
-	C_{3,5\times5} & C_{4,5\times5}
-	\end{pmatrix}, \quad \textbf{D}_{t,10\times9}= \begin{pmatrix}
-	D_{1,5\times5} & D_{2,5\times4} \\
-	D_{3,5\times5} & D_{4,5\times4}
-	\end{pmatrix}\notag \\
-	\widetilde{\textbf{F}}_{t,10\times10}=\begin{pmatrix}
-	F_{1,5\times5} & F_{2,5\times5} \\
-	F_{3,5\times5} & F_{4,5\times5}
-	\end{pmatrix}, \quad 	\widetilde{\textbf{G}}_{t,10\times10}= \begin{pmatrix}
-	G_{1,5\times5} & G_{2,5\times5} \\
-	G_{3,5\times5} & G_{4,5\times5}
-	\end{pmatrix}\notag 
-	\end{align}
-	of the system 
-   \begin{align}
-   \textbf{V}_t &= \textbf{A}^{-1}\left[\widetilde{\textbf{B}}_t\textbf{V}_{t-1}+\widetilde{\textbf{C}}_t\textbf{V}_{t-2}+\widetilde{\textbf{F}}_t\widetilde{\text{E}}^{anc}_{t-1}\widetilde{\textbf{V}}_{t}+\widetilde{\textbf{G}}_t\textbf{V}^{avg.}_{t-1}+\textbf{D}\textbf{e}_t\right],
-   \end{align}
-   \newpage
-	\section{Questionaire}
-	Here you can include a questionnaire that you used in your paper.
-\end{appendix}
-\newpage
-\section*{Affirmation}
-I hereby declare that I have composed my Bachelor/Master's thesis / Seminar paper 
-\textit{"title"} independently using only those resources mentioned, 
-and that I have as such identified all passages which I have 
-taken from publications verbatim or in substance. I agree that the work will be reviewed using plagiarism testing software.
-Neither 
-this paper, nor any extract of it, has been previously 
-submitted to an examining authority, in this or a similar 
-form.\\ \\
-\textit{Only for Bacherlor’s and Master’s theses with included CD:}\\
-I have ensured that the written version of this thesis is 
-identical to the version saved on the enclosed storage 
-medium. \\\\\\
 

### 2022-08-23 markov_model.R

@@ -9,12 +9,14 @@ lret = diff(log(price))[-1,]
 plot(lret)
 
 
+lret = lret*100
+
 split_idx = round(length(lret)*0.9)
+y = lret
 train_y = lret[1:split_idx]
 test_y = lret[(1+split_idx):length(lret)]
 
-real_vola = abs(lret*100)
-
+real_vol = abs(lret)
 
 
 #HMM
@@ -22,28 +24,74 @@ library("MSGARCH")
 
 # SINGLE REGIME
 
+# ---------------------- Training the models -----------------------------------
+# ------------------------------------------------------------------------------
+
+
 
 # MULTI-REGIME (non-switching shape)
 ms2.garch.n <- CreateSpec(variance.spec = list(model = c("tGARCH", "tGARCH")),
                    distribution.spec = list(distribution = c("sged", "sged")))
 summary(ms2.garch.n)
-fit.ml <- FitML(spec = ms2.garch.n, data = train_y*100)
+fit.ml <- FitML(spec = ms2.garch.n, data = train_y)
 summary(fit.ml)
 
-fit.mcmc <- FitMCMC(spec = ms2.garch.n, data = train_y)
-summary(fit.mcmc)
-
-# Forecasting
-last_date = 10
-pred <- predict(fit.ml, nahead = 5, do.return.draw = TRUE, newdata=test_y[0:last_date])
-
-date = index(pred$draw[1, ])
-date
-lret[date]
 
 
-pred <- predict(fit.mcmc, nahead = 1, do.return.draw = FALSE)
-pred
+# ---------------------- Creating Point Forecasts ------------------------------
+# ------------------------------------------------------------------------------
+horizons = c(1,5)
+fcst <- xts(x = cbind(replicate(length(horizons), rep(-1, length(test_y)))), 
+               order.by = index(test_y))
+names(fcst) = sapply(horizons, function(x) paste("h_d", toString(x)))
+
+
+for (dd in 1:length(test_y)) {
+  pred <- predict(fit.ml, nahead = max(horizons), do.return.draw = FALSE, newdata=test_y[1:dd])
+  fcst[dd,] = pred$vol[horizons]
+}  
+msgarch_fcst <- fcst
+
+plot(msgarch_fcst[, 2])
+lines(msgarch_fcst[, 1])
+lines(real_vol[index(msgarch_fcst)], col="red")
+
+
+# --------------- Point Forecast evaluation etc. -------------------------------
[…]

### 2022-09-20 markov_model.R
Adds ggplot2 graphs and imports OMI library data

@@ -1,10 +1,16 @@
 # Import Dataset
 library("quantmod")
+library(ggplot2)
+library(dplyr)
+library(latex2exp)
 
-start <- as.Date("1950-01-01")
+data_dir = "C:\\Users\\Adria\\Documents\\Github Projects\\data\\markov-switching"
+
+start <- as.Date("1988-01-05")
 end <- as.Date("2022-08-21")
 df <- quantmod::getSymbols("^SP500TR", src = "yahoo", from = start, to = end, auto.assign = FALSE)
 price = df[, "SP500TR.Close"]
+colnames(price) <- "Price"
 lret = diff(log(price))[-1,]
 plot(lret)
 
@@ -18,6 +24,14 @@ test_y = lret[(1+split_idx):length(lret)]
 
 real_vol = abs(lret)
 
+
+# Imports realized volatility 
+omi <- read.csv(paste(data_dir, "\\oxfordmanrealizedvolatilityindices.csv", sep=""))
+omi <- omi[omi$Symbol==".SPX", ]
+omi$Date <- as.Date(omi$X)
+plot(omi$rk_parzen*sqrt(250))
+
+omi_vol <- xts(select(omi, "rk_parzen"), order.by=as.Date(omi[, 21]))
 
 #HMM
 library("MSGARCH")
@@ -36,14 +50,30 @@ summary(ms2.garch.n)
 fit.ml <- FitML(spec = ms2.garch.n, data = train_y)
 summary(fit.ml)
 
+# Unconditional volatility levels
+sqrt(250) * sapply(ExtractStateFit(fit.ml), UncVol)
+
+# Predicted in-sample Probabilities
+fit.ml.state <- State(fit.ml)
+pred_probs <- fit.ml.state$PredProb[, 1, 1]
+pred_probs <- data.frame(Dates = as.Date(names(pred_probs)), value=pred_probs) # Convert to data.frame for ggplot2
+ggplot() + 
+  geom_line(data=pred_probs, aes(x=Dates, y=value, group=1)) + 
+  scale_x_date(date_breaks = "years" , date_labels = "%y") + 
+  xlab("Dates (Year)") + 
+  ylab("Prob") + 
+  ggtitle("Predicted in-sample Probability of state 1") + 
+  theme(plot.title = element_text(hjust = 0.5))
 
 
 # ---------------------- Creating Point Forecasts ------------------------------
 # ------------------------------------------------------------------------------
+start.time <- Sys.time()
+
 horizons = c(1,5)
[…]

### 2022-09-21 LaTeX/MSGARCH.tex
Adds some latex and scenario graphs

--- 2022-08-23 LaTeX/Vorlage Latex - Eng.tex
@@
 
+% HINZUGEFÜGT VON ADRIAN
 % MAKE subsubsubsection possible
 \usepackage{titlesec}
+\usepackage{cleveref}
+\usepackage{acronym}
+
+\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
+\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
+\newacro{ARMA}{AutoRegressive Moving Average}
+\newacro{SGED}{Skewed Generlized Error Distribution}
 
@@
 
+\subsubsection{Heavy-tailed Distributions}
+Many different distributions have been suggested for modeling asset returns, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions.
+In this paper we will use the \ac{GED}, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered.
+$$f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}$$
+
 \subsubsection{GARCH}
-GARCH (General Autoregressive Conditional Heteroskedasticity) has been popular in order to forecast the volatility of indices.
-It tries to explain the observation that the volatility of an asset tends to cluster, i.e.
-periods with high volatility are followed by periods with high volatility.
-however the model fails to explain many phenomena which are observed, like the fat-tailedness of drawdown periods and depths (cite Robert Frey).
+\label{sss:GARCH}
+The \ac{GARCH} model has been popular in order to forecast the volatility of indices.
+It was introduced XXXX by \cite{} and is an extension of the ARCH model, which was introduced Engle \cite{}.
+It models the error by using a \ac{ARMA} model.
+It tries to explain the observation that the volatility of financial assets tends to be heteroskedastic and cluster, i.e. periods with high volatility are followed by periods with high volatility.
+
 The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
-$$y_{l} \mid\left(s_{l}=k, \mathcal{I}_{l-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$
-$\mathcal{D}$ being some zero-mean distribution, the variance h and shape parameters $\xi$.
+Denote $y_t$ the log-returns in time period $t$, i.e. $log(p_t-p_{t-1})$ if $p_t$ is the asset price at time t.
+
+$$y_{t} \mid\left(s_{t}=k, \mathcal{I}_{t-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$
+
+$\mathcal{D}$ being some zero-mean distribution, the conditional variance$h_{k,t}$ in state $k$ at time $t$ and shape parameters $\xi$.
 For short time-periods the zero-mean specification is justified most of the time.
@@
 
-A GARCH(1,1) model has the form $h_{k, t} \equiv \alpha_{0, k}+\alpha_{1, k} y_{t-1}^{2}+\beta_{k} h_{k, t-1}$.
-Similar to an ARMA model which tries specify the conditional mean, the GARCH model tries to specify the conditional variance.
+A GARCH(1,1) model has the form $h_{k, t} \equiv \alpha_{0, k}+\alpha_{1, k} y_{t-1}^{2}+\beta_{k} h_{k, t-1}$ models the conditional variance process.
+$h_{k,t}$ is the conditional variance.
+Similar to an \ac{ARMA} model which tries specify the conditional mean, the \ac{GARCH} model tries to specify the conditional variance.
 The lagged squared return term can be interpreted as a proxy for the realized variance in the last observation period.
-Long periods of high variance can be modeled by increasing the intercept $\beta$.\\
+In this model long periods of high variance can be modeled by increasing the intercept $\beta$.\\
 
-Many extensions of the GARCH model exist, like (todo).
-The TGARCH e.g.
-tries to incorporate the observation that variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
-$$h_{k, t}^{1 / 2} \equiv \alpha_{0, k}+\left(\alpha_{1, k} \mathbb{I}\left\{y_{t-1} \geq 0\right\}-\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}+\beta_{k} h_{k, t-1}^{1 / 2}$$
+Many extensions of the GARCH model exist which try to account for the the observation that the variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
+One example is the GJR model by \cite{}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$
+
+However the GARCH model fails to explain many phenomena which are observed, like the fat-tailedness of drawdown periods and depths (cite Robert Frey).
 
@@
 3. A markov-switching model with indicators
+
+For the GARCH as well as for the MSGARCH models we will use a \ac{SGED} to describe the distribution of the log-returns.
+Also, GJR-GARCH is used for both of the models, see \cref{sss:GARCH}.
 

### 2022-09-21 markov_model.R

@@ -3,103 +3,168 @@ library("quantmod")
 library(ggplot2)
 library(dplyr)
 library(latex2exp)
+library("MSGARCH")
+library(patchwork)
+require(gridExtra)
+
+theme_update(plot.title = element_text(hjust = 0.5))
+msgarch_color = "green"
+garch_color = "red"
+
+# TODO: Include random walk error
 
 data_dir = "C:\\Users\\Adria\\Documents\\Github Projects\\data\\markov-switching"
+img_dir = "C:\\Users\\Adria\\Documents\\Github Projects\\markov-regime-switching\\LaTeX\\img"
 
-start <- as.Date("1988-01-05")
+start <- as.Date("1900-01-05")
 end <- as.Date("2022-08-21")
-df <- quantmod::getSymbols("^SP500TR", src = "yahoo", from = start, to = end, auto.assign = FALSE)
-price = df[, "SP500TR.Close"]
+df <- quantmod::getSymbols("^GSPC", src = "yahoo", from = start, to = end, auto.assign = FALSE)
+price = df[, "GSPC.Close"]
 colnames(price) <- "Price"
 lret = diff(log(price))[-1,]
 plot(lret)
 
 
-lret = lret*100
+corona_indices <- seq.Date(as.Date("2020-01-01"),as.Date("2022-05-01"),by="day")
+housing_bubble <- seq.Date(as.Date("2008-01-01"),as.Date("2010-01-01"),by="day")
+russia_war <- seq.Date(as.Date("2021-01-01"),as.Date("2023-01-01"),by="day")
+oil <- seq.Date(as.Date("1986-01-01"),as.Date("1991-01-01"),by="day")
 
-split_idx = round(length(lret)*0.9)
+lret = lret*100 # For numerical purposes
+
+split_idx = round(length(lret)*0.8)
 y = lret
 train_y = lret[1:split_idx]
 test_y = lret[(1+split_idx):length(lret)]
 
 real_vol = abs(lret)
+train_vol = real_vol[1:split_idx]
+test_vol = real_vol[(1+split_idx):length(lret)]
 
 
-# Imports realized volatility 
-omi <- read.csv(paste(data_dir, "\\oxfordmanrealizedvolatilityindices.csv", sep=""))
-omi <- omi[omi$Symbol==".SPX", ]
-omi$Date <- as.Date(omi$X)
-plot(omi$rk_parzen*sqrt(250))
-
[…]

### 2022-09-24 LaTeX/MSGARCH.tex
...

@@
 \usepackage{titlesec}
+
 \usepackage{cleveref}
@@
 
+\graphicspath{{./img/}}
+
+% ACRONYMS 
 \newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
@@
 \newacro{SGED}{Skewed Generlized Error Distribution}
+\newacro{GED}{Generlized Error Distribution}
 
@@
 
+$$ \mathcal{L}\left(\Psi \mid \mathcal{I}_T\right) \equiv \prod_{t=1}^T f\left(y_t \mid \Psi, \mathcal{I}_{t-1}\right) $$ 
 \subsection{Markov-Switching Models}
@@
 The \ac{GARCH} model has been popular in order to forecast the volatility of indices.
-It was introduced XXXX by \cite{} and is an extension of the ARCH model, which was introduced Engle \cite{}.
+It was introduced  by Bollerslev \cite{bollerslev_generalized_1986} and is an extension of the ARCH model, which was introduced Engle \cite{engle_autoregressive_1982}.
 It models the error by using a \ac{ARMA} model.
@@
 Many extensions of the GARCH model exist which try to account for the the observation that the variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
-One example is the GJR model by \cite{}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$
+One example is the GJR model by \cite{glosten_relation_1993}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$
 
@@
 \subsection{Data set}
+The GARCH model assumes that the datapoints are equidistant in the time dimension, hence we will use the closing prices of the Index and model the close-to-close variance.
+
+We split our dataset s.t. we use the first 80\% observations for training and the last 20\% for testing the models.
 
 \subsection{Results}
+
+% latex table generated in R 4.1.2 by xtable 1.8-4 package
+% Thu Sep 22 19:29:22 2022
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & MSSR1 & MSSR2 & GARCH \\ 
+  \hline
+$\alpha\_1$ & 0.17 & 0.00 & 0.01 \\ 
+  alpha1\_1 & 0.02 & 0.02 & 0.03 \\ 
+  alpha2\_1 & 0.21 & 0.08 & 0.08 \\ 
+  beta\_1 & 0.75 & 0.94 & 0.92 \\ 
+  nu\_1 & 1.05 & 1.53 & 6.19 \\ 
+  xi\_1 & 0.86 & 0.96 & 0.93 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\subsubsection{Evaluation of Point Forecasts}
+
+\begin{figure}[h]
+\includegraphics[width=0.8\linewidth]{pforecast-russia-crash.pdf}
+\caption{One-day-ahead volatility forecasts during the Corona crash 2020.}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=1.2\linewidth]{FiltVola\_InSample\_Eighties.pdf}
+\caption{One-day-ahead volatility forecasts during the Corona crash 2020. MSGARCH is model mostly in state 1.}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=1.2\linewidth]{CoronaCrash\_MSGARCH\_Decomposition.pdf}
+\caption{One-day-ahead volatility forecasts during the Corona crash 2020. MSGARCH is model mostly in state 1.}
+\label{img:cor-decomp}
+\end{figure}
+
+In \cref{img:cor-decomp} one can see the two states of the MSGARCH (MSSR1 and MSSR2) model produce different forecasts and how they compare to the stand-alone GARCH model. 
+It can be observed that MSSR1 is less persistent, which is due to the smaller $\beta_1 = 0.7519$ compared to the larger $\beta_2 = 0.935$ of MSSR2.
+Furthermore we see that MSSR1 has a higher base-level volatility and tends to forecast volatility spikes which are larger than those of MSSR2.
+This once again, is caused by the larger $\alpha$ values which characterise MSSR1.
 

### 2022-09-24 markov_model.R

@@ -6,12 +6,21 @@ library(latex2exp)
 library("MSGARCH")
 library(patchwork)
 require(gridExtra)
+library(murphydiagram)
+library(forecast)
+library(xtable)
+library(fGarch)
+
 
 theme_update(plot.title = element_text(hjust = 0.5))
 msgarch_color = "green"
 garch_color = "red"
+mssr1_color = "brown"
+mssr2_color = "blue"
 
-# TODO: Include random walk error
+# TODO: Include scatter plot of returns/ Realized Vola
+# TODO: Analyze Subsample performance
+# TODO: Compare special state performance
 
 data_dir = "C:\\Users\\Adria\\Documents\\Github Projects\\data\\markov-switching"
 img_dir = "C:\\Users\\Adria\\Documents\\Github Projects\\markov-regime-switching\\LaTeX\\img"
@@ -22,13 +31,11 @@ df <- quantmod::getSymbols("^GSPC", src = "yahoo", from = start, to = end, auto.
 price = df[, "GSPC.Close"]
 colnames(price) <- "Price"
 lret = diff(log(price))[-1,]
+lret = lret - mean(lret) # Demeaning -> MSGARCH assumption
 plot(lret)
 
 
-corona_indices <- seq.Date(as.Date("2020-01-01"),as.Date("2022-05-01"),by="day")
-housing_bubble <- seq.Date(as.Date("2008-01-01"),as.Date("2010-01-01"),by="day")
-russia_war <- seq.Date(as.Date("2021-01-01"),as.Date("2023-01-01"),by="day")
-oil <- seq.Date(as.Date("1986-01-01"),as.Date("1991-01-01"),by="day")
+
 
 lret = lret*100 # For numerical purposes
 
@@ -46,6 +53,16 @@ bear_test_dates <- c(seq.Date(as.Date("2020-02-01"),as.Date("2020-04-01"),by="da
                      seq.Date(as.Date("2021-01-01"),as.Date("2023-01-01"),by="day"))
 bull_test_dates <- index(test_vol)[!(index(test_vol) %in% bear_test_dates)]
   
+
+corona_indices <- seq.Date(as.Date("2020-01-01"),as.Date("2022-05-01"),by="day")
+housing_bubble <- seq.Date(as.Date("2008-01-01"),as.Date("2010-01-01"),by="day")
[…]

### 2022-09-24 markov_model.R
Adding structure to the R file

@@ -12,6 +12,41 @@ library(xtable)
 library(fGarch)
 
 
+
+# Helpful Functions -------------------------------------------------------
+f_mse <- function(y_hat, y) {
+  return (mean((y_hat - y)^2))
+}
+f_mae <- function(y_hat, y) {
+  return (mean(abs(y_hat - y)))
+}
+f_bias <- function(y_hat, y) {
+  return (mean(y_hat - y))
+}
+f_rmse <- function(y_hat, y) {
+  return (sqrt(f_mse(y_hat, y)))
+}
+get_err_table <- function(y_hat, y) {
+  if (is.null(dim(y_hat))) {
+    mse <- f_mse(y_hat, y)
+    mae <- f_mae(y_hat, y)
+    bias <- f_bias(y_hat, y)
+    rmse <- f_rmse(y_hat, y) 
+  } else {
+    mse <- sapply(y_hat, f_mse, y)
+    mae <- sapply(y_hat, f_mae, y)
+    bias <- sapply(y_hat, f_bias, y)
+    rmse <- sapply(y_hat, f_rmse, y)  
+  }
+  err_table <- cbind(mse, mae, rmse, bias)
+  return(err_table)
+}
+
+
+# Section 1 ---------------------------------------------------------------
+
+
+
 theme_update(plot.title = element_text(hjust = 0.5))
 msgarch_color = "green"
 garch_color = "red"
@@ -46,7 +81,9 @@ test_y = lret[(1+split_idx):length(lret)]
 
 real_vol = abs(lret)
 train_vol = real_vol[1:split_idx]
+train_var = train_vol^2
 test_vol = real_vol[(1+split_idx):length(lret)]
+test_var = test_vol^2
 
 
 bear_test_dates <- c(seq.Date(as.Date("2020-02-01"),as.Date("2020-04-01"),by="day"),
@@ -76,8 +113,12 @@ eighties <- seq.Date(as.Date("1986-01-01"),as.Date("1990-01-01"),by="day")
 # 
 # test_omi_vol <- omi_vol[index(test_vol)]
 
-# ---------------------- Training the models -----------------------------------
-# ------------------------------------------------------------------------------
+
+
+
+
+# Training the Models and Preliminary Analysis ----------------------------
+
 set.seed(420)
 
 # Training the models took approx. 1 min
@@ -168,8 +209,10 @@ ggsave(paste(img_dir, "\\FiltVola_InSample_Eighties.pdf", sep=""))
 #grid.arrange(p1, p2, nrow=2)
 
 
[…]

### 2022-09-25 LaTeX/MSGARCH.tex
Checkpoint

@@
 \newacro{GED}{Generlized Error Distribution}
+\newacro{MSE}{mean-square error}
+\newacro{MAE}{mean-absolute error}
+\newacro{RMSE}{root-mean-square error}
 
@@
 \subsection{Experiment description}
-We compare the performance of 3 models: 
-1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
-2. A markov-switching model without indicators
-3. A markov-switching model with indicators
+We compare the performance of 2 models a stand-alone GARCH model and a MSGARCH model
 
@@
 Also, GJR-GARCH is used for both of the models, see \cref{sss:GARCH}.
+
+\subsubsection{Performance Measures}
+When measuring the performance one has to be careful not to compare the square root variance forecasts $\sqrt{h_t}$ with the absolute returns $\sqrt{y_t^2} = | y_t |$ as these would be biased due to Jensen's inequality: Our model tries to achieve $\mathbb{V}(y) =\mathbb{E}(y^2) = h$ and $\mathbb{E}(| y |) \neq \sqrt{h}$.
+Instead the variance $h_t$ should be compared to the squared returns $y_t^2$.
+
+The actual measures we employ are the following: \ac{MSE}, \ac{MAE}, \ac{RMSE}
 
@@
 \subsection{Results}
+\subsubsection{Analysis of Model Parameters}
+In \cref{tab:model-params} the model parameters are displayed, which were fitted using a maximum likelihood estimator and the training set.
 
@@
 \begin{table}[ht]
+\label{tab:model-params}
 \centering
@@
 \subsubsection{Evaluation of Point Forecasts}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrr}
+  \hline
+ & mse & mae & rmse & bias \\ 
+  \hline
+MSGARCH\_h1 & 24.2096 & 1.5169 & 4.9203 & 0.0195 \\ 
+  GARCH\_h1 & 24.9891 & 1.5415 & 4.9989 & 0.0441 \\ 
+  MSSR1\_h1 & 25.2808 & 1.5446 & 5.0280 & 0.0380 \\ 
+  MSSR\_h1 & 25.2808 & 1.5446 & 5.0280 & 0.0380 \\ 
+  Avg & 33.6508 & 1.8815 & 5.8009 & -0.0301 \\ 
+   \hline
+\end{tabular}
+\end{table}
 

### 2022-09-25 markov_model.R

@@ -12,8 +12,8 @@ library(xtable)
 library(fGarch)
 
 
-
 # Helpful Functions -------------------------------------------------------
+
 f_mse <- function(y_hat, y) {
   return (mean((y_hat - y)^2))
 }
@@ -44,9 +44,6 @@ get_err_table <- function(y_hat, y) {
 
 
 # Section 1 ---------------------------------------------------------------
-
-
-
 theme_update(plot.title = element_text(hjust = 0.5))
 msgarch_color = "green"
 garch_color = "red"
@@ -143,7 +140,7 @@ sr.fit <- ExtractStateFit(msgarch.fit.ml)
 params <- cbind(sr.fit[[1]]$par, sr.fit[[2]]$par, garch.fit.ml$par)
 params <- as.data.frame(params)
 colnames(params) <- c("MSSR1", "MSSR2", "GARCH")
-xtable(params)
+xtable(params, label="tab:model-params", caption="Fitted parameters of the MSGARCH and the GARCH model.")
 
 # Visualize densities
 f <- function(x) { return(dsged(x, 0, 1, nu=params[5, 1], xi=params[4, 1])) }
@@ -212,15 +209,13 @@ ggsave(paste(img_dir, "\\FiltVola_InSample_Eighties.pdf", sep=""))
 
 # Generating Point Forecasts ----------------------------------------------
 
-
-
-# Calculating the Point forecasts took approx. 1 min.
+# 3 Minutes for all Points forecasts...
 
 horizons = 1:10 # currently only works for horizon=1!!
 
-start.time <- Sys.time()
 
-testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), max(horizons))
+
+testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), 1)
 
 
 # -------------------- MSGARCH and GARCH
@@ -247,22 +242,38 @@ testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), max(horizons))
 # }
 
 # ---------------------- Single regime
+
+
 fcst <- xts(x = cbind(replicate(length(horizons), rep(-1, length(test_y)))), 
             order.by = index(test_y))
 names(fcst) = sapply(horizons, function(x) paste("GARCH_h", toString(x), sep=""))
 
[…]

### 2022-09-25 markov_model.R
Making multi-step ahead forecasts and save-load code

@@ -1,9 +1,9 @@
 # Import Dataset
-library("quantmod")
+library(quantmod)
 library(ggplot2)
 library(dplyr)
 library(latex2exp)
-library("MSGARCH")
+library(MSGARCH)
 library(patchwork)
 require(gridExtra)
 library(murphydiagram)
@@ -114,7 +114,15 @@ eighties <- seq.Date(as.Date("1986-01-01"),as.Date("1990-01-01"),by="day")
 
 
 
-# Training the Models and Preliminary Analysis ----------------------------
+# Training the Models ----------------------------------------------------------
+
+# Option: Execute this and skip rest of section
+load("fitted_models.RData")
+msgarch.fit.ml$spec = CreateSpec()
+sr.fit[[1]]$spec = CreateSpec()
+sr.fit[[2]]$spec = CreateSpec()
+garch.fit.ml$spec = CreateSpec()
+#---
 
 set.seed(420)
 
@@ -135,6 +143,11 @@ summary(ms2.garch.n)
 msgarch.fit.ml <- FitML(spec = ms2.garch.n, data = train_y)
 summary(msgarch.fit.ml)
 sr.fit <- ExtractStateFit(msgarch.fit.ml)
+
+save(list=c("msgarch.fit.ml", "sr.fit", "garch.fit.ml"), file="fitted_models.RData")
+
+
+# Preliminary Analysis ---------------------------------------------------------
 
 # Make LaTeX table of parameters
 params <- cbind(sr.fit[[1]]$par, sr.fit[[2]]$par, garch.fit.ml$par)
@@ -209,12 +222,11 @@ ggsave(paste(img_dir, "\\FiltVola_InSample_Eighties.pdf", sep=""))
 
 # Generating Point Forecasts ----------------------------------------------
 
-# 3 Minutes for all Points forecasts...
+# Option: Load old forecasts and skip this section
+#load("point_forecasts.RData")
+
 
 horizons = 1:10 # currently only works for horizon=1!!
-
-
-
 testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), 1)
 
 
@@ -242,8 +254,6 @@ testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), 1)
 # }
 
 # ---------------------- Single regime
-
-
 fcst <- xts(x = cbind(replicate(length(horizons), rep(-1, length(test_y)))), 
[…]

### 2022-09-26 markov_model.R
Adds first evaluation of multi-step forecasts

@@ -11,6 +11,7 @@ library(forecast)
 library(xtable)
 library(fGarch)
 
+# Set working directory to this file's directory.
 
 # Helpful Functions -------------------------------------------------------
 
@@ -27,6 +28,14 @@ f_rmse <- function(y_hat, y) {
   return (sqrt(f_mse(y_hat, y)))
 }
 get_err_table <- function(y_hat, y) {
+  # This assumes the last column has the least entries, i.e. largest forecasting horizon
+  y_hat <- y_hat[y_hat[, ncol(y_hat)] > 0, ] 
+  new_idx <- intersect(index(y_hat), index(y))
+  y_hat <- y_hat[index(y_hat) %in% new_idx,]
+  y <- y[index(y) %in% new_idx]
+  
+  stopifnot(nrow(y_hat) == length(y))
+  
   if (is.null(dim(y_hat))) {
     mse <- f_mse(y_hat, y)
     mae <- f_mae(y_hat, y)
@@ -222,12 +231,15 @@ ggsave(paste(img_dir, "\\FiltVola_InSample_Eighties.pdf", sep=""))
 
 # Generating Point Forecasts ----------------------------------------------
 
-# Option: Load old forecasts and skip this section
-#load("point_forecasts.RData")
-
-
 horizons = 1:10 # currently only works for horizon=1!!
 testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), 1)
+
+
+# Option: Load old forecasts and skip this section
+load("point_forecasts.RData")
+
+
+
 
 
 # -------------------- MSGARCH and GARCH
@@ -355,7 +367,24 @@ dm.test(msgarch_fcst[,1]^2, garch_fcst[,1]^2, h=1, power = 2)
 murphydiagram(as.vector(msgarch_fcst[,1]), as.vector(garch_fcst[,1]), as.vector(test_vol$Price), labels=c("MSGARCH", "GARCH"))
 
 # Point Forecast Evaluation - Out-of-Sample - multi-step --------
-print("TODO")
+avg_fcst <- test_var
+avg_fcst[index(avg_fcst)] = mean(train_var)
+
+msgarch_mserr <- get_err_table(msgarch_fcst^2, test_var)
+garch_mserr <- get_err_table(garch_fcst^2, test_var)
+avg_err <- get_err_table(avg_fcst, test_var)
+rownames(avg_err) = "Avg"
[…]

### 2022-09-26 markov_model.R
Checkpoint

@@ -27,7 +27,7 @@ f_bias <- function(y_hat, y) {
 f_rmse <- function(y_hat, y) {
   return (sqrt(f_mse(y_hat, y)))
 }
-get_err_table <- function(y_hat, y) {
+get_err_table <- function(y_hat, y, agg_funcs=list) {
   # This assumes the last column has the least entries, i.e. largest forecasting horizon
   y_hat <- y_hat[y_hat[, ncol(y_hat)] > 0, ] 
   new_idx <- intersect(index(y_hat), index(y))
@@ -53,7 +53,7 @@ get_err_table <- function(y_hat, y) {
 
 
 # Section 1 ---------------------------------------------------------------
-theme_update(plot.title = element_text(hjust = 0.5))
+theme_update(plot.title = element_text(hjust = 0.5), legend.position = "bottom")
 msgarch_color = "green"
 garch_color = "red"
 mssr1_color = "brown"
@@ -183,8 +183,9 @@ ggsave(paste(img_dir, "\\FittedStandardizedDistr.pdf", sep=""))
 
 
 # Unconditional volatility levels
-sqrt(250) * sapply(ExtractStateFit(msgarch.fit.ml), UncVol)
-sqrt(250) * sapply(ExtractStateFit(garch.fit.ml), UncVol)
+sapply(ExtractStateFit(msgarch.fit.ml), UncVol)
+sapply(ExtractStateFit(garch.fit.ml), UncVol)
+sqrt(mean(train_var))
 
 end.time <- Sys.time()
 time.taken <- end.time - start.time
@@ -343,7 +344,7 @@ save(list=c("msgarch_fcst", "garch_fcst", "sr1_fcst", "sr2_fcst", # Point Foreca
            "train_vol", "test_vol"), file="point_forecasts.RData")
 
 # Point Forecast Evaluation
-# Point Forecast Evaluation - Out-of-Sample - single-step --------
+# Point Forecast Evaluation - Out-of-Sample - Single-step --------
 msgarch_err <- get_err_table(msgarch_fcst[,1]^2, test_var)
 garch_err <- get_err_table(garch_fcst[,1]^2, test_var)
 sr1_err <- get_err_table(sr1_fcst^2, test_var)
@@ -366,7 +367,12 @@ dm.test(msgarch_fcst[,1]^2, garch_fcst[,1]^2, h=1, power = 2)
[…]

### 2022-09-26 markov_model.R
Checkpoint

@@ -15,6 +15,7 @@ library(fGarch)
 
 # Helpful Functions -------------------------------------------------------
 
+
 f_mse <- function(y_hat, y) {
   return (mean((y_hat - y)^2))
 }
@@ -27,14 +28,16 @@ f_bias <- function(y_hat, y) {
 f_rmse <- function(y_hat, y) {
   return (sqrt(f_mse(y_hat, y)))
 }
-get_err_table <- function(y_hat, y, agg_funcs=list) {
+get_err_table <- function(y_hat, y, agg_funcs=list("MSE"=f_mse, "MAE"=f_mae, "RMSE"=f_rmse, "BIAS"=f_bias)) {
   # This assumes the last column has the least entries, i.e. largest forecasting horizon
-  y_hat <- y_hat[y_hat[, ncol(y_hat)] > 0, ] 
+  y_hat <- y_hat[(is.na(y_hat) %>% rowSums)==0, ] 
   new_idx <- intersect(index(y_hat), index(y))
   y_hat <- y_hat[index(y_hat) %in% new_idx,]
   y <- y[index(y) %in% new_idx]
   
   stopifnot(nrow(y_hat) == length(y))
+  stopifnot(is.na(y_hat) == 0)
+  stopifnot(min(y_hat) > 0)
   
   if (is.null(dim(y_hat))) {
     mse <- f_mse(y_hat, y)
@@ -42,10 +45,8 @@ get_err_table <- function(y_hat, y, agg_funcs=list) {
     bias <- f_bias(y_hat, y)
     rmse <- f_rmse(y_hat, y) 
   } else {
-    mse <- sapply(y_hat, f_mse, y)
-    mae <- sapply(y_hat, f_mae, y)
-    bias <- sapply(y_hat, f_bias, y)
-    rmse <- sapply(y_hat, f_rmse, y)  
+    func <- function(f){return(sapply(y_hat, f, y))}
+    return(sapply(agg_funcs, func))
   }
   err_table <- cbind(mse, mae, rmse, bias)
   return(err_table)
@@ -162,7 +163,7 @@ save(list=c("msgarch.fit.ml", "sr.fit", "garch.fit.ml"), file="fitted_models.RDa
 params <- cbind(sr.fit[[1]]$par, sr.fit[[2]]$par, garch.fit.ml$par)
 params <- as.data.frame(params)
 colnames(params) <- c("MSSR1", "MSSR2", "GARCH")
[…]

### 2022-09-28 LaTeX/MSGARCH.tex
Start Evaluation in LaTeX and adjust plots in markov_model.R

@@
 \usepackage{acronym}
-
+\usepackage[toc,page]{appendix}
+\usepackage{subfig}
 \graphicspath{{./img/}}
+\usepackage{caption}
 
@@
 
-$$y_{t} \mid\left(s_{t}=k, \mathcal{I}_{t-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$
+\begin{equation} \label{eq:msgarch-spec}
+	y_{t} \mid\left(s_{t}=k, \mathcal{I}_{t-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \Psi_{k}\right)
+\end{equation}
 
@@
 Many extensions of the GARCH model exist which try to account for the the observation that the variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
-One example is the GJR model by \cite{glosten_relation_1993}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$
+One example is the GJR model by \cite{glosten_relation_1993}:
+\begin{equation} \label{eq:GJR}
+	h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}
+\end{equation}
 
@@
 
-\section{First chapter of main text}
-We try to predict S\&P index using
+\section{Markov-Switching GARCH}
 
 \subsection{Experiment description}
-We compare the performance of 2 models a stand-alone GARCH model and a MSGARCH model
+In this work we train, evaulate and compare two models for forecasting the density and especially the volatility of future S\&P500 stock returns.
 
-For the GARCH as well as for the MSGARCH models we will use a \ac{SGED} to describe the distribution of the log-returns.
-Also, GJR-GARCH is used for both of the models, see \cref{sss:GARCH}.
+We compare the performance of 2 models, namely a single-state and a two-state markov-switching GARCH model.
+Henceforth these will be denoted as GARCH and MSGARCH (Markov-Switching GARCH) respectively.
+The two individual states in the MSGARCH model will be called MSSR1 and MSSR2, which abbreviates Markov-Switching Single-Regime $k$.
+
+For the single-state as well as for the markov-switching models we will use a \ac{SGED} to describe the distribution of the log-returns.
+For the GARCH model as well as for both states of the MSGARCH model, the GJR-GARCH specification is used, in order to make results easily interpretable and comparable.
 
@@
 
-The actual measures we employ are the following: \ac{MSE}, \ac{MAE}, \ac{RMSE}
+The actual measures we employ are the following: \ac{MSE}, \ac{MAE}, \ac{RMSE}.
 
@@
 The GARCH model assumes that the datapoints are equidistant in the time dimension, hence we will use the closing prices of the Index and model the close-to-close variance.
+Both for numerical reasons as well as for the ease of interpretation we will use the log-returns multiplied by 100 for training the model and for the evaluation.
 
@@
 \subsection{Results}
-\subsubsection{Analysis of Model Parameters}
-In \cref{tab:model-params} the model parameters are displayed, which were fitted using a maximum likelihood estimator and the training set.
+\subsubsection{Analysis of Model Behaviour and Parameters}
+In \cref{tab:model-params} the model parameters for the (MS-)GARCH model (see \cref{eq:GJR}) and shape parameters $\Psi = (\nu, \xi)$ of the conditional distribution (see ) are displayed, which were fitted using a maximum likelihood estimator on the training set.
+The two separate states from the MSGARCH model are denoted MSSR1 and MSSR2.
+%TODO: Describe characteristics of MSSR1, MSSR2 and GARCH.
+XXXX is likely to play a role after large volatility spikes like the 1987 Black Monday (see XXXX).
 
 % latex table generated in R 4.1.2 by xtable 1.8-4 package
-% Thu Sep 22 19:29:22 2022
-\begin{table}[ht]
-\label{tab:model-params}
-\centering
+% Tue Sep 27 12:14:13 2022
+\vspace{0.5cm}
+\begin{minipage}[c]{0.5\textwidth}
 	\begin{tabular}{rrrr}
@@
 		\hline
-$\alpha\_1$ & 0.17 & 0.00 & 0.01 \\ 
-  alpha1\_1 & 0.02 & 0.02 & 0.03 \\ 
-  alpha2\_1 & 0.21 & 0.08 & 0.08 \\ 
-  beta\_1 & 0.75 & 0.94 & 0.92 \\ 
-  nu\_1 & 1.05 & 1.53 & 6.19 \\ 
-  xi\_1 & 0.86 & 0.96 & 0.93 \\ 
+		$\alpha_{0,1}$ & 0.0042 & 0.1680 & 0.0082 \\ 
+		$\alpha_{1,1}$ & 0.0214 & 0.0168 & 0.0356 \\ 
+		$\alpha_{2,1}$ & 0.0781 & 0.2072 & 0.0741 \\ 
+		$\beta_1$ & 0.9347 & 0.7483 & 0.9207 \\ 
+		$\nu_1$ & 1.5314 & 1.0446 & 1.3168 \\ 
+		$\xi_1$ & 0.9680 & 0.8731 & 0.9329 \\ 
 		\hline
 	\end{tabular}
-\end{table}
+	\captionof{table}{Fitted model and shape parameters.}
+	 \label{tab:model-params}
+\end{minipage}
+\begin{minipage}[c]{0.5\textwidth}
+	\begin{tabular}{lrr} 
+		\hline
+		& $t+1 | k=1$ & $t+1 | k=2$ \\
+		\hline
+		$t | k=1$ & 0.9983 & 0.0017 \\
+		$t | k=2$ & 0.0059 & 0.9941 \\
+		\hline
+	\end{tabular}
+	\captionof{table}{Transitions probabilities of the MSGARCH states.}
+ 	\label{tab:trans-probs}
+\end{minipage}
+\vspace{0.5cm}
+
+In \cref{tab:trans-probs} the transitions probabilities for the states in the MSGARCH model are displayed.
+The stable probabilities (i.e.
+the long-term probability of being in state 1 or 2) are XXXX for MSSR1 and XXXX for MSSR2.
+
+In \cref{img:single-state-forecasts} one can see the two states of the MSGARCH (MSSR1 and MSSR2) model produce different forecasts and how they compare to the stand-alone GARCH model. 
+It can be observed that MSSR1 is less persistent, which is due to the smaller $\beta_1 = 0.7519$ compared to the larger $\beta_2 = 0.935$ of MSSR2.
+Furthermore we see that MSSR1 has a higher base-level volatility and tends to forecast volatility spikes which are larger than those of MSSR2.
+This once again, is caused by the larger $\alpha$ values which characterise MSSR1.
+
+\begin{figure}[H]
+	\label{img:single-state-forecasts}
+	\includegraphics[width=\linewidth]{CoronaCrash_MSGARCH_Decomposition.pdf}
+	\caption{One-day-ahead volatility forecasts during the Corona crash 2020. }
+\end{figure}
 
@@
 
-\begin{table}[ht]
+\begin{figure}[H]
 	\centering
-\begin{tabular}{rrrrr}
-  \hline
- & mse & mae & rmse & bias \\ 
-  \hline
-MSGARCH\_h1 & 24.2096 & 1.5169 & 4.9203 & 0.0195 \\ 
-  GARCH\_h1 & 24.9891 & 1.5415 & 4.9989 & 0.0441 \\ 
-  MSSR1\_h1 & 25.2808 & 1.5446 & 5.0280 & 0.0380 \\ 
-  MSSR\_h1 & 25.2808 & 1.5446 & 5.0280 & 0.0380 \\ 
-  Avg & 33.6508 & 1.8815 & 5.8009 & -0.0301 \\ 
-   \hline
-\end{tabular}
-\end{table}
+	\label{fig:oos-error-multi-step}
+	\includegraphics[width=\textwidth]{Forecast-Errors-OOS-Multi-Step.pdf}
+	\caption{Out-of-sample error measurements for different forecasting horizons and the two models MSGARCH and GARCH.}
+\end{figure}
+
+In \cref{fig:oos-error-multi-step} we can see that MSGARCH has outperformed the GARCH model out-of-sample for every forecasting horizon from 1 to 10 days and for both measures MAE and MSE. 
+A similar plot was generated using the RMSE error measure, which isn't displayed here for brevity, but can be verified in \cref{app:point-forecasts}. 
+The percentage-wise improvement $\frac{e_{GARCH}-e_{MSGARCH}}{e_{GARCH}}$ (where e is the error measure) ranges from 2.14\% to 4\% for MSE and from 0.81\% to 3.2\% for MAE.
+It is not large, but consistent across error measures and forecasting horizons.
+Both errors increase linearly with respect to the forecasting horizon, tending towards the error obtained by the unconditional volatility estimate.
 
 \begin{figure}[h]
-\includegraphics[width=0.8\linewidth]{pforecast-russia-crash.pdf}
+\includegraphics[width=1.2\linewidth]{pforecast-russia-crash.pdf}
 \caption{One-day-ahead volatility forecasts during the Corona crash 2020.}
@@
 \end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=1.2\linewidth]{CoronaCrash\_MSGARCH\_Decomposition.pdf}
-\caption{One-day-ahead volatility forecasts during the Corona crash 2020. MSGARCH is model mostly in state 1.}
-\label{img:cor-decomp}
-\end{figure}
-
-In \cref{img:cor-decomp} one can see the two states of the MSGARCH (MSSR1 and MSSR2) model produce different forecasts and how they compare to the stand-alone GARCH model. 
-It can be observed that MSSR1 is less persistent, which is due to the smaller $\beta_1 = 0.7519$ compared to the larger $\beta_2 = 0.935$ of MSSR2.
-Furthermore we see that MSSR1 has a higher base-level volatility and tends to forecast volatility spikes which are larger than those of MSSR2.
-This once again, is caused by the larger $\alpha$ values which characterise MSSR1.
 
@@
 
+\begin{appendices}
+\chapter{Point Forecasts}
+\label{app:point-forecasts}
+
+\end{appendices}
+
 \newpage

### 2022-09-28 markov_model.R

@@ -10,6 +10,8 @@ library(murphydiagram)
 library(forecast)
 library(xtable)
 library(fGarch)
+library(gridExtra)
+library(cowplot)
 
 # Set working directory to this file's directory.
 
@@ -54,6 +56,8 @@ get_err_table <- function(y_hat, y, agg_funcs=list("MSE"=f_mse, "MAE"=f_mae, "RM
 
 
 # Section 1 ---------------------------------------------------------------
+save_plots = FALSE
+
 theme_update(plot.title = element_text(hjust = 0.5), legend.position = "bottom")
 msgarch_color = "green"
 garch_color = "red"
@@ -154,7 +158,11 @@ msgarch.fit.ml <- FitML(spec = ms2.garch.n, data = train_y)
 summary(msgarch.fit.ml)
 sr.fit <- ExtractStateFit(msgarch.fit.ml)
 
-save(list=c("msgarch.fit.ml", "sr.fit", "garch.fit.ml"), file="fitted_models.RData")
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+time.taken
+
+#save(list=c("msgarch.fit.ml", "sr.fit", "garch.fit.ml"), file="fitted_models.RData")
 
 
 # Preliminary Analysis ---------------------------------------------------------
@@ -180,17 +188,15 @@ ggplot() +
   ggtitle("Fitted standardized distributions for the log-returns") +
   ylab("f(y)") +
   xlab("y")
-ggsave(paste(img_dir, "\\FittedStandardizedDistr.pdf", sep=""))
+if (save_plots) ggsave(paste(img_dir, "\\FittedStandardizedDistr.pdf", sep=""))
 
+# Analysis of tails 
+# Log-log plot
 
 # Unconditional volatility levels
 sapply(ExtractStateFit(msgarch.fit.ml), UncVol)
 sapply(ExtractStateFit(garch.fit.ml), UncVol)
 sqrt(mean(train_var))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-time.taken
 
 # MSGARCH only: in-sample Probabilities
 msgarch.fit.ml.state <- State(msgarch.fit.ml)
@@ -208,7 +214,7 @@ p1 <- ggplot() +
[…]

### 2022-09-28 markov_model.R
Calculates CRPS

@@ -12,11 +12,20 @@ library(xtable)
 library(fGarch)
 library(gridExtra)
 library(cowplot)
+library(scoringRules)
 
 # Set working directory to this file's directory.
 
 # Helpful Functions -------------------------------------------------------
-
+my_map <- function(xs, fs) {
+  #f hast to be a list
+  res <- rep(NA, length(fs))
+  for (ii in 1:length(fs)) {
+    res[ii] <- fs[[ii]](xs[ii])
+  }
+  return(res)
+}
+  
 
 f_mse <- function(y_hat, y) {
   return (mean((y_hat - y)^2))
@@ -139,8 +148,6 @@ garch.fit.ml$spec = CreateSpec()
 #---
 
 set.seed(420)
-
-# Training the models took approx. 1 min
 start.time <- Sys.time()
 
 # SINGLE-REGIME 
@@ -155,13 +162,14 @@ ms2.garch.n <- CreateSpec(variance.spec = list(model = c("gjrGARCH", "gjrGARCH")
                    distribution.spec = list(distribution = c("sged", "sged")))
 summary(ms2.garch.n)
 msgarch.fit.ml <- FitML(spec = ms2.garch.n, data = train_y)
+
 summary(msgarch.fit.ml)
-sr.fit <- ExtractStateFit(msgarch.fit.ml)
 
 end.time <- Sys.time()
 time.taken <- end.time - start.time
 time.taken
 
+sr.fit <- ExtractStateFit(msgarch.fit.ml)
 #save(list=c("msgarch.fit.ml", "sr.fit", "garch.fit.ml"), file="fitted_models.RData")
 
 
@@ -238,37 +246,39 @@ if (save_plots) ggsave(paste(img_dir, "\\FiltVola_InSample_Eighties.pdf", sep=""
 
 
 # Generating Point Forecasts ----------------------------------------------
-
-horizons = 1:10 # currently only works for horizon=1!!
+set.seed(420)
+horizons = 1:10
 testing_anchor_points <- seq(1, (length(test_y)-max(horizons)), 1)
-
 
 # Option: Load old forecasts and skip this section
 #load("point_forecasts.RData")
 
 
 # Generating Point Forecasts - Single regime (GARCH) ---------------------------
-
[…]

### 2022-09-28 LaTeX/MSGARCH.tex
Adds murphydiagrams

@@
 \usepackage[toc,page]{appendix}
-\usepackage{subfig}
+%\usepackage{subfig}
 \graphicspath{{./img/}}
 \usepackage{caption}
+\usepackage[yyyymmdd]{datetime}
+\usepackage{subcaption}
+%\usepackage[demo]{graphicx}
 
@@
 \newacro{SGED}{Skewed Generlized Error Distribution}
-\newacro{GED}{Generlized Error Distribution}
+\newacro{GED}{Generalized Error Distribution}
 \newacro{MSE}{mean-square error}
@@
 \newacro{RMSE}{root-mean-square error}
+\newacro{MSM}{Markov-Switching Model}
+\newacro{HMM}{Hidden Markov Model}
 
@@
 		\textbf{} & \\
-		$\pi$ & rate of inflation\\
-		$i$ & nominal interest rate \\
-		$r$ & real interest rate \\
-		$M$ & money stock \\
-
+		$\sigma$ & standard deviation\\
+		$\Psi$ & set of parameter values \\
+		$h$ conditional variance
 	\end{tabular}\\ \vspace{1cm}
@@
 \section{Background}
+\subsection{Markov-Switching Models}
+The general model consists of two stochastic processes $X$ and $Y$.
+The process $Y$ is observed, e.g.
+the stock price of a company, and it's conditional distribution depends on the unobserved Markov chain process $X$.
+According to \cite{an_identifiability_2013}, when the distribution of $y_t$ depends only on $x_t$ it is called a \ac{HMM}, and if it additionally depends  on the lagged values $y_{t-1}, ...
+y_{t-l}$ we call it a \ac{MSM}.
 
@@
 $$ \mathcal{L}\left(\Psi \mid \mathcal{I}_T\right) \equiv \prod_{t=1}^T f\left(y_t \mid \Psi, \mathcal{I}_{t-1}\right) $$
-\subsection{Markov-Switching Models}
 
@@
 
-\subsection{Financial Market Data}
+\subsection{Financial Markets}
 
@@
 
-\subsubsection{Heavy-tailed Distributions}
-Many different distributions have been suggested for modeling asset returns, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions.
-In this paper we will use the \ac{GED}, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered.
+\subsubsection{Distributions}
+Many different distributions have been suggested for modeling asset returns and volatility, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions. 
+In this paper we will consider the (Log-)normal, the \ac{GED} and the Student-t distribution, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered distribution.
+The following three distributions are in standardized form, i.e.
+they are centered around 0 and have a standard deviation of 1.
+
+\paragraph{Normal Distribution}
+$$f_N(\eta) \equiv \frac{1}{\sqrt{2 \pi}} e^{-\frac{1}{2} \eta^2}$$
+
+\paragraph{Generalized Error Distribution}
 $$f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}$$
+\paragraph{Student-t Distribution}
+$$f_S(\eta ; \nu) \equiv \frac{\Gamma\left(\frac{\nu+1}{2}\right)}{\sqrt{(\nu-2) \pi} \Gamma\left(\frac{\nu}{2}\right)}\left(1+\frac{\eta^2}{(\nu-2)}\right)^{-\frac{\nu+1}{2}}$$
 
@@
 
-The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
+The Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
 Denote $y_t$ the log-returns in time period $t$, i.e. $log(p_t-p_{t-1})$ if $p_t$ is the asset price at time t.
@@
 
+For training the model and producing the forecasts we use the R package 'MSGARCH' (version 2.50) by \cite{ardia_markov-switching_2019}.
+
 \subsubsection{Performance Measures}
@@
 
-\subsection{Data set}
+\subsubsection{Data set}
+Our data set
+
 The GARCH model assumes that the datapoints are equidistant in the time dimension, hence we will use the closing prices of the Index and model the close-to-close variance.
@@
 \subsection{Results}
+\subsubsection{Model Selection}
+
 \subsubsection{Analysis of Model Behaviour and Parameters}
@@
 	\end{tabular}
-	\captionof{table}{Transitions probabilities of the MSGARCH states.}
+	\captionof{table}{Transition probabilities of the MSGARCH states.}
  	\label{tab:trans-probs}
@@
 
-In \cref{tab:trans-probs} the transitions probabilities for the states in the MSGARCH model are displayed.
+In \cref{tab:trans-probs} the transitions probabilities for the markov chain states in the MSGARCH model are displayed.
 The stable probabilities (i.e.
@@
 
-\subsubsection{Evaluation of Point Forecasts}
+%TODO insample performance evaluation ?
+
+\subsubsection{Out-of-Sample Evaluation}
+We evaluated the performance of our model in an out-of-sample dataset ranging from \formatdate{02}{10}{2003} to \formatdate{19}{08}{2022}.
+For every date we produce point and density forecasts via simulation with a forecasting horizon ranging from 1 to 10 trading days.
 
@@
 Both errors increase linearly with respect to the forecasting horizon, tending towards the error obtained by the unconditional volatility estimate.
+
+% TODO: Diebold-Mariano test
+
+In \cref{fig:murphy-diagrams} the difference of the two forecasts in the murphy diagram are displayed.
+It can't be observed that any forecasting model dominates the other.
+This means that it depends on the error measure, whether the single-state GARCH or the MSGARCH forecasts produce smaller, more desireable quantities.
+For an explanation of murphy diagrams, see \cite{ehm_quantiles_2016} Sections 3 and 4.
+
+\begin{figure}[H]
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{murph1.pdf}
+		\caption{1a}
+		\label{fig:sfig1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{murph2.pdf}
+		\caption{1b}
+		\label{fig:sfig2}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=.8\linewidth]{murph3.pdf}
+	\caption{1b}
+	\label{fig:sfig2}
+\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=.8\linewidth]{murph4.pdf}
+	\caption{1b}
+	\label{fig:sfig2}
+\end{subfigure}
+	\caption{Plots showing the difference in the extremal scores of the MSGARCH and the GARCH forecasts for horizons 1-4.}
+	\label{fig:murphy-diagrams}
+\end{figure}
+
+% TODO CRPS analysis
 
@@
 \begin{appendices}
+%TODO add tables here
 \chapter{Point Forecasts}

### 2022-09-28 markov_model.R

@@ -14,7 +14,10 @@ library(gridExtra)
 library(cowplot)
 library(scoringRules)
 
+
 # Set working directory to this file's directory.
+# install.packages("gridGraphics")
+# Add `return(recordPlot())` at the bottom of trace("murphydiagram_diff",edit=TRUE)
 
 # Helpful Functions -------------------------------------------------------
 my_map <- function(xs, fs) {
@@ -40,32 +43,31 @@ f_rmse <- function(y_hat, y) {
   return (sqrt(f_mse(y_hat, y)))
 }
 get_err_table <- function(y_hat, y, agg_funcs=list("MSE"=f_mse, "MAE"=f_mae, "RMSE"=f_rmse, "BIAS"=f_bias)) {
-  # This assumes the last column has the least entries, i.e. largest forecasting horizon
-  y_hat <- y_hat[(is.na(y_hat) %>% rowSums)==0, ] 
-  new_idx <- intersect(index(y_hat), index(y))
-  y_hat <- y_hat[index(y_hat) %in% new_idx,]
-  y <- y[index(y) %in% new_idx]
-  
-  stopifnot(nrow(y_hat) == length(y))
-  stopifnot(is.na(y_hat) == 0)
-  stopifnot(min(y_hat) > 0)
   
   if (is.null(dim(y_hat))) {
-    mse <- f_mse(y_hat, y)
-    mae <- f_mae(y_hat, y)
-    bias <- f_bias(y_hat, y)
-    rmse <- f_rmse(y_hat, y) 
+    # for in-sample evaluation...
+    func_1d <- function(f){return(f(y_hat, y))}
+    return(sapply(agg_funcs, func_1d))
+    
   } else {
+    # This assumes the last column has the least entries, i.e. largest forecasting horizon
+    y_hat <- y_hat[(is.na(y_hat) %>% rowSums)==0, ] 
+    new_idx <- intersect(index(y_hat), index(y))
+    y_hat <- y_hat[index(y_hat) %in% new_idx,]
+    y <- y[index(y) %in% new_idx]
+    
+    stopifnot(nrow(y_hat) == length(y))
+    stopifnot(is.na(y_hat) == 0)
+    stopifnot(min(y_hat) > 0)
+    
     func <- function(f){return(sapply(y_hat, f, y))}
     return(sapply(agg_funcs, func))
   }
-  err_table <- cbind(mse, mae, rmse, bias)
-  return(err_table)
 }
 
 
[…]

### 2022-09-28 markov_model.R
Adds bootstrap confidence intervals

@@ -17,7 +17,6 @@ library(scoringRules)
 
 # Set working directory to this file's directory.
 # install.packages("gridGraphics")
-# Add `return(recordPlot())` at the bottom of trace("murphydiagram_diff",edit=TRUE)
 
 # Helpful Functions -------------------------------------------------------
 my_map <- function(xs, fs) {
@@ -141,12 +140,12 @@ eighties <- seq.Date(as.Date("1986-01-01"),as.Date("1990-01-01"),by="day")
 
 # Training the Models ----------------------------------------------------------
 
-# Option: Execute this and skip rest of section
-load("fitted_models.RData")
-msgarch.fit.ml$spec = CreateSpec()
-sr.fit[[1]]$spec = CreateSpec()
-sr.fit[[2]]$spec = CreateSpec()
-garch.fit.ml$spec = CreateSpec()
+# Option: Execute this and skip rest of section (doesnt quite work atm ?)
+# load("fitted_models.RData")
+# msgarch.fit.ml$spec = CreateSpec()
+# sr.fit[[1]]$spec = CreateSpec()
+# sr.fit[[2]]$spec = CreateSpec()
+# garch.fit.ml$spec = CreateSpec()
 #---
 
 set.seed(420)
@@ -365,19 +364,19 @@ dm.test(msgarch_fcst[,1]^2, garch_fcst[,1]^2, h=1, power = 2)
 end = (length(msgarch_fcst[, 1])-max(horizons)-1)
 start = max(horizons)+1
 
-p1 <- murphydiagram_diff(as.vector(msgarch_fcst[1:cutoff,1]^2), 
+murphydiagram_diff(as.vector(msgarch_fcst[1:cutoff,1]^2), 
               as.vector(garch_fcst[1:cutoff,1]^2), 
               as.vector(test_var$Price)[1:cutoff],)
 title("h=1")
 p1 <- recordPlot()
 
-p2 <- murphydiagram_diff(as.vector(msgarch_fcst[start:cutoff,2]^2), 
+murphydiagram_diff(as.vector(msgarch_fcst[start:cutoff,2]^2), 
                    as.vector(garch_fcst[start:cutoff,2]^2), 
                    as.vector(test_var$Price)[start:cutoff],)
 title("h=2")
 p2 <- recordPlot()
 
[…]

### 2022-10-06 LaTeX/MSGARCH.tex
save

@@
 \usepackage{titlesec}
-
+\usepackage[nottoc]{tocbibind}
 \usepackage{cleveref}
@@
 \usepackage{subcaption}
+\usepackage{bbm}
 %\usepackage[demo]{graphicx}
@@
 % ACRONYMS 
+\newacro{MSGARCH}{Markov-Switching GARCH}
 \newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
@@
 \newacro{HMM}{Hidden Markov Model}
+\newacro{CRPS}{Continuous Ranked Probability Score}
+\newacro{cdf}{cumulative density function}
+\newacro{MSM}{markov-switching models}
 
@@
 Markov chain processes can be useful for identifying regimes in the past as well as estimating the current regime. %% why is this important
-If the Markov model describes the data generating process well, it can also be used to simulate synthetic time series and potential future paths. %% why is this important
+If the \ac{MSM} describes the data generating process well, it can also be used to simulate synthetic time series and potential future paths. %% why is this important
+
+\ac{MSM}s have been a popular approach in modelling non-linear time series dynamics.
+
+\ac{GARCH} models are widely used in order to describe the behaviour of financial time series.
+In this work we want to assess in a case study, if a markov-switching will improve the forecasts of a stand-alone GARCH model.
 
@@
 Many different distributions have been suggested for modeling asset returns and volatility, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions. 
-In this paper we will consider the (Log-)normal, the \ac{GED} and the Student-t distribution, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered distribution.
-The following three distributions are in standardized form, i.e.
-they are centered around 0 and have a standard deviation of 1.
-
-\paragraph{Normal Distribution}
-$$f_N(\eta) \equiv \frac{1}{\sqrt{2 \pi}} e^{-\frac{1}{2} \eta^2}$$
+In this paper we will consider  \ac{GED}, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered distribution.
 
 \paragraph{Generalized Error Distribution}
-$$f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}$$
-\paragraph{Student-t Distribution}
-$$f_S(\eta ; \nu) \equiv \frac{\Gamma\left(\frac{\nu+1}{2}\right)}{\sqrt{(\nu-2) \pi} \Gamma\left(\frac{\nu}{2}\right)}\left(1+\frac{\eta^2}{(\nu-2)}\right)^{-\frac{\nu+1}{2}}$$
+\begin{equation} \label{eq:ged}
+f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}
+\end{equation}
+where $\nu$ is the shape parameter and $\lambda$ the scale parameter the density function.
+
+\paragraph{Skewness}
+Since the densities of financial stochastic processes are usually skewed, a method of introducing this property to the symmetric density \cref{eq:ged} is required.
+Given a standardized, symmetric unimodal density, Trottier and Ardia suggest the following transformation, which doesn't change neither the mean nor the variance (see \cite{trottier_moments_2015}).
+The degree of skewness is parametrized by $0<\xi<\infty$:
+\begin{equation} \label{eq:skewness}
+	f_{\xi}(z) \equiv \frac{2 \sigma_{\xi}}{\xi+\xi^{-1}} f_1\left(z_{\xi}\right), \quad z_{\xi} \equiv \begin{cases}\xi^{-1}\left(\sigma_{\xi} z+\mu_{\xi}\right) & \text { if } z \geq-\mu_{\xi} / \sigma_{\xi} \\ \xi\left(\sigma_{\xi} z+\mu_{\xi}\right) & \text { if } z<-\mu_{\xi} / \sigma_{\xi}\end{cases}
+\end{equation} 
+where $\mu_{\xi} \equiv M_1\left(\xi-\xi^{-1}\right), \quad \sigma_{\xi}^2 \equiv\left(1-M_1^2\right)\left(\xi^2+\xi^{-2}\right)+2 M_1^2-1, \quad M_1 \equiv 2 \int_0^{\infty} u f_1(u) d u$. .
+
+\subsection{Error Measures}\label{sec:error-measures}
+
+\subsubsection*{\ac{MSE}}
+\begin{equation}
+	\operatorname{MSE}=\frac{\sum_{t=1}^T\left(\hat{y}_t-y_t\right)^2}{T}
+\end{equation}
+
+\subsubsection*{\ac{MAE}}
+\begin{equation}
+	\operatorname{MAE}=\frac{\sum_{t=1}^T |\hat{y}_t-y_t |}{T}
+\end{equation}
+
+\subsubsection*{\ac{RMSE}}
+\begin{equation}
+	\operatorname{RMSE}=\sqrt{\frac{\sum_{t=1}^T\left(\hat{y}_t-y_t\right)^2}{T}}
+\end{equation}
+
+\subsubsection*{\ac{CRPS}}
+The \ac{CRPS} is defined as:
+\begin{equation}
+	\operatorname{CRPS}(F_t, y_t)=\int_{\mathbb{R}}[F(x) - \mathbbm{1} (x \geq y_t)]^2 \mathrm{~d} x
+\end{equation}
+Herer $F_t$ is the predicted \ac{cdf} for $y_t$, the observed value.
+The average CRPS over a set of observations can then be used as an error measure.
+One of the advantages of the CRPS is that it doesn't require a density and can handle distributions with point mass such as the empirical \ac{cdf}.
 
@@
 
-The actual measures we employ are the following: \ac{MSE}, \ac{MAE}, \ac{RMSE}.
+The actual measures we employ are the following: \ac{MSE}, \ac{MAE}, \ac{RMSE} and the average \ac{CRPS}, see \cref{sec:error-measures}.
 
 \subsubsection{Data set}
-Our data set
+The data set consists of the SPX daily close ranging from \formatdate{03}{01}{1928} to \formatdate{21}{08}{2022}. The data is obtained from Yahoo Finance\footnote{https://finance.yahoo.com/}.
+
+This data set is split s.t. the first 80\% observations are used for training and the last 20\% for testing the models.
 
@@
 
-We split our dataset s.t. we use the first 80\% observations for training and the last 20\% for testing the models.
-
 \subsection{Results}
-\subsubsection{Model Selection}
 
 \subsubsection{Analysis of Model Behaviour and Parameters}
+
+%TODO add insample state probabilities
+
 In \cref{tab:model-params} the model parameters for the (MS-)GARCH model (see \cref{eq:GJR}) and shape parameters $\Psi = (\nu, \xi)$ of the conditional distribution (see ) are displayed, which were fitted using a maximum likelihood estimator on the training set.
@@
 The stable probabilities (i.e.
-the long-term probability of being in state 1 or 2) are XXXX for MSSR1 and XXXX for MSSR2.
+the long-term probability of being in state 1 or 2) are 77.32\% for MSSR1 and 22.68\% for MSSR2.
+
+\begin{figure}[H]
+	\begin{subfigure}{1\textwidth}
+	\centering
+	\includegraphics[width=0.7\linewidth]{FittedStandardizedDistr.pdf}
+	\caption{Probability distribution functions}
+	\end{subfigure} \\
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{FittedStandardizedDistrLogLogRight.pdf}
+		\caption{Log-log plot for the positive tails}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{FittedStandardizedDistrLogLogLeft.pdf}
+	\caption{Log-log-plot for the negative tails} \label{fig:distributions-left-tail}
+	\end{subfigure}
+	\caption{}
+	\label{fig:distributions}
+\end{figure}
+
+In \cref{fig:distributions} the probability density functions of each sate and their tail behaviours are displayed.
+In the log-log-plots one observe see the heavier tails of MSSR2 compared to the other two densities, especially in the negative tail.
 
@@
 We evaluated the performance of our model in an out-of-sample dataset ranging from \formatdate{02}{10}{2003} to \formatdate{19}{08}{2022}.
-For every date we produce point and density forecasts via simulation with a forecasting horizon ranging from 1 to 10 trading days.
+For every date the point and density forecasts are produced via simulation with a forecasting horizon ranging from 1 to 10 trading days.
+For this purpose 10000 future paths with length 10 are simulated at each step.
 
 \begin{figure}[H]
+	\label{fig:oos-error-multi-step}
+	\begin{subfigure}{1.2\textwidth}
 	\centering
-	\label{fig:oos-error-multi-step}
 	\includegraphics[width=\textwidth]{Forecast-Errors-OOS-Multi-Step.pdf}
+	\end{subfigure}
+
+	\begin{subfigure}{1.2\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{Forecast-Errors-OOS-Multi-Step2.pdf}
+	\end{subfigure}
 	\caption{Out-of-sample error measurements for different forecasting horizons and the two models MSGARCH and GARCH.}
@@
 
-In \cref{fig:oos-error-multi-step} we can see that MSGARCH has outperformed the GARCH model out-of-sample for every forecasting horizon from 1 to 10 days and for both measures MAE and MSE. 
-A similar plot was generated using the RMSE error measure, which isn't displayed here for brevity, but can be verified in \cref{app:point-forecasts}. 
+In \cref{fig:oos-error-multi-step} we can see that MSGARCH has slightly outperformed the GARCH model out-of-sample for every forecasting horizon from 1 to 10 days and for the three measures \ac{MSE}, \ac{MAE} and \ac{RMSE}.
+The density forecasts were even more similar in performance, here the GARCH model even  achieved slightly lower, i.e.
+better \ac{CRPS} values.
+
 The percentage-wise improvement $\frac{e_{GARCH}-e_{MSGARCH}}{e_{GARCH}}$ (where e is the error measure) ranges from 2.14\% to 4\% for MSE and from 0.81\% to 3.2\% for MAE.
@@
 
-% TODO: Diebold-Mariano test
+%TODO: Error intervals
 
@@
 It can't be observed that any forecasting model dominates the other.
-This means that it depends on the error measure, whether the single-state GARCH or the MSGARCH forecasts produce smaller, more desireable quantities.
-For an explanation of murphy diagrams, see \cite{ehm_quantiles_2016} Sections 3 and 4.
+This means that it depends on the error measure, whether the single-state GARCH or the MSGARCH forecasts produce smaller, more desireable errors.
+Neither forecast is strictly better for all scoring rules which are consistent for the mean. For an explanation of murphy diagrams, see \cite{ehm_quantiles_2016} Sections 3 and 4.
 
@@
 		\caption{1a}
-		\label{fig:sfig1}
 	\end{subfigure}%
@@
 		\caption{1b}
-		\label{fig:sfig2}
 	\end{subfigure}
@@
 	\caption{1b}
-	\label{fig:sfig2}
 \end{subfigure}
@@
 
-% TODO CRPS analysis
+\subsection{Subsample Performance}
+We further analyze the performance for two subsamples, which are categorized into a bull market and a bear market. For the bear market subsample we take the periods of 
+\formatdate{22}{01}{2008} \textendash \formatdate{08}{07}{2009}, \formatdate{01}{02}{2020} \textendash \formatdate{13}{04}{2020} and \formatdate{01}{01}{2022} \textendash \formatdate{21}{08}{2022}.
 
-\begin{figure}[h]
-\includegraphics[width=1.2\linewidth]{pforecast-russia-crash.pdf}
-\caption{One-day-ahead volatility forecasts during the Corona crash 2020.}
+\subsubsection{Bear Markets}
+\begin{figure}[H]
+	\label{fig:bear-error-multi-step}
+	\begin{subfigure}{1.2\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Forecast-Errors-BEAR-Multi-Step.pdf}
+	\end{subfigure}
+
+	\begin{subfigure}{1.2\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Forecast-Errors-BEAR-Multi-Step2.pdf}
+	\end{subfigure}
+	\caption{Out-of-sample bear market subsample error measurements for different forecasting horizons and the two models MSGARCH and GARCH.}
 \end{figure}
 
-\begin{figure}[h]
-\includegraphics[width=1.2\linewidth]{FiltVola\_InSample\_Eighties.pdf}
-\caption{One-day-ahead volatility forecasts during the Corona crash 2020. MSGARCH is model mostly in state 1.}
+% TODO: Add scenario pictures
+
+\subsubsection{Bull Markets}
+\begin{figure}[H]
+	\label{fig:bull-error-multi-step}
+	\begin{subfigure}{1.2\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Forecast-Errors-BULL-Multi-Step.pdf}
+	\end{subfigure}
+
+	\begin{subfigure}{1.2\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Forecast-Errors-BULL-Multi-Step2.pdf}
+	\end{subfigure}
+	\caption{Out-of-sample bull market subsample error measurements for different forecasting horizons.}
 \end{figure}
@@
 \section{Conclusion}
+In this work the compared and analyzed the forecasting performance of a GARCH model with a \ac*{MSGARCH} for the S\&P using daily returns ranging from 1928 to 2022.
+We evaluated density forecasts as well as point forecasts for the volatility for different forecasting horizons.
+In this experiment we didn't see any significant evidence that would suggest that the markov-switching model produced superior forecasts compared to the single-regime \ac{GARCH} model.
+More experiments will have to be performed, including different model specifications, time horizons and indices in order to evaluate, if the markov-switching approach adds value in this setting.
 
@@
 \newpage
-\addcontentsline{toc}{section}{Bibliography}
-\section*{Bibliography}
-In the bibliography, you list all the sources that you use and therefore cite in the text (sources that you have read but not cited should not be listed).
-Sort the entries in the bibliography, listed according to a consistent style, alphabetically by last name.
-
 \bibliography{References}

### 2022-10-06 markov_model.R

@@ -107,17 +107,19 @@ test_vol = real_vol[(1+split_idx):length(lret)]
 test_var = test_vol^2
 
 
-bear_test_dates <- c(seq.Date(as.Date("2020-02-01"),as.Date("2020-04-01"),by="day"),
-                     seq.Date(as.Date("2021-01-01"),as.Date("2023-01-01"),by="day"))
+russia_war <- seq.Date(as.Date("2021-01-01"),as.Date("2022-08-19"),by="day")
+bear_test_dates <- c(seq.Date(as.Date("2008-01-22"),as.Date("2009-07-08"),by="day"),
+                     seq.Date(as.Date("2020-02-01"),as.Date("2020-04-13"),by="day"),
+                     russia_war)
 bull_test_dates <- index(test_vol)[!(index(test_vol) %in% bear_test_dates)]
   
 
-corona_indices <- seq.Date(as.Date("2020-01-01"),as.Date("2022-05-01"),by="day")
+corona_indices <- seq.Date(as.Date("2020-01-01"),as.Date("2021-01-01"),by="day")
 housing_bubble <- seq.Date(as.Date("2008-01-01"),as.Date("2010-01-01"),by="day")
-russia_war <- seq.Date(as.Date("2021-01-01"),as.Date("2023-01-01"),by="day")
+
+bull_example <- seq.Date(as.Date("2016-01-01"), as.Date("2018-01-01"),by="day")
+
 oil <- seq.Date(as.Date("1986-01-01"),as.Date("1991-01-01"),by="day")
-
-
 eighties <- seq.Date(as.Date("1986-01-01"),as.Date("1990-01-01"),by="day")
 
 
@@ -194,13 +196,46 @@ ggplot() +
   geom_line(aes(x=x_grid, y=sapply(x_grid, h), color="GARCH")) + 
   scale_color_manual(name = "Model", 
                      values = c("GARCH"=garch_color, "MSSR1"=mssr1_color, "MSSR2"=mssr2_color)) + 
-  ggtitle("Fitted standardized distributions for the log-returns") +
+  #ggtitle("Fitted standardized distributions for the log-returns") +
   ylab("f(y)") +
   xlab("y")
[…]
